%%% A template to produce a nice-looking Curriculum Vitae.
%%% Originally from Kieran Healy <kjhealy@gmail.com>
%%% Kieran's source is at http://kjhealy.github.com/kjh-vita
%%%
%%% This source code has been adapted by
%%% Ben Marwick <benmarwick@gmail.com> and is largely
%%% determined by the instructions here:
%%% https://admin.artsci.washington.edu/promotion-and-tenure-documentation#curriculum
%%%

%%% ------------------------------------------------------------------------
%%% Requirements for this document that are included
%%%  in (or otherwise easily obtained) a modern tex distribution:
%%% ------------------------------------------------------------------------
%%% xelatex (I'm using MiKTeX & Texmaker)
%%% fontspec.sty
%%% hyperrref.sty
%%% xunicode.sty
%%% color.sty
%%% url.sty
%%% fancyhdr.sty
%%% memoir.cls
%%% fontawesome.sty
%%% gitinfo.sty
%%%
%%%
%%% ------------------------------------------------------------------------
%%% Requirements from https://github.com/kjhealy/latex-custom-kjh
%%% ------------------------------------------------------------------------
%%% org-preamble-xelatex.sty
%%% memoir-article-styles.sty
%%%
%%%
%%% ------------------------------------------------------------------------
%%% Note
%%%------------------------------------------------------------------------
%%% Because this is a hand-tweaked file, be on the look out for \medksip,
%%% \bigskip and \newpage commands here and there, which are used to balance
%%% the layout or avoid widows & orphans, etc. You should of course add or
%%% remove these as needed.
%%%------------------------------------------------------------------------

\documentclass[11pt,article,oneside]{memoir}
\usepackage{microtype}
\usepackage{org-preamble-xelatex}
\newfontfamily\fontawesome[Extension=.otf]{FontAwesome}
\usepackage{fontawesome,url}
\usepackage{setspace}
\usepackage[footinfo]{gitinfo2}
\usepackage{xeCJK} %% for the Japanese characters
\setCJKmainfont[BoldFont=NotoSansCJKjp-Bold,AutoFakeSlant=0.15]{Noto Sans CJK JP} %% for the Japanese character



%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------

%% Change as needed.
\def\myauthor{Ben Marwick}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
%%%%%%%%  UW details
% \def\myaffiliation{University of Washington}
% \def\myaddress{Anthropology Department}
% \def\myemail{bmarwick@uw.edu}
% \def\myweb{http://faculty.washington.edu/bmarwick/ }
% \def\myphone{(206) 552-9450}
% \def\myfax{(206) 543-3285}
% \def\mytwitter{@benmarwick}
% \def\myversion{}
% \def\myrevision{}

%%%%%%%%  UOW details
\def\myaffiliation{University of Wollongong}
\def\myaddress{School of Earth and Environmental Sciences}
\def\myemail{bmarwick@uow.edu.au}
\def\myphone{(02) 4221 5455}
\def\mytwitter{@benmarwick}


\def\myversion{}
\def\myrevision{}


%%%%%%%%  UW details
% \def\myaffiliation{University of Washington}
%%%%%%%%  UOW details
\def\myaffiliation{University of Wollongong}
\def\myauthor{Ben Marwick}
\date{} % not used (revision control instead)
\def\mykeywords{}




%%%------------------------------------------------------------------------
%%% Document
%%%------------------------------------------------------------------------
\begin{document}

%% Choose fonts for use with xelatex
%% Using free fonts with big glyph sets for maximum flexibility
%% http://www.linuxlibertine.org/index.php?id=2&L=1
%% http://font.ubuntu.com/

\setromanfont[Mapping={tex-text},
	Numbers={OldStyle},
	Ligatures={Common}]{Linux Libertine}
\setsansfont[Mapping=tex-text,
	Ligatures={Common},
	Colour=AA0000]{Linux Biolinum}
\setmonofont[Mapping=tex-text,Scale=0.72]{Ubuntu}

\newfontface\scheader[SmallCapsFont={Linux Libertine},SmallCapsFeatures={Letters=SmallCaps}]{Linux Libertine}

\newfontface\addressblock[Mapping={tex-text},
	Numbers={OldStyle},
	Ligatures={Common}]{Linux Libertine}


%%%------------------------------------------------------------------------
%%% Local commands
%%%------------------------------------------------------------------------

%% Marginal header
%% Note: as the document goes on you may need to introduce a (gradually increasing)
%% \vspace element to keep the marginal header pleasingly aligned with the first
%% item in the body text. Like this: \marginhead{{\vskip 0.4em}Grants}, or
%% \marginhead{{\vskip 0.8em}Service}. Experiment as needed.
\newcommand{\marginhead}[1]{\marginpar{\textsf{{\footnotesize\vspace{-1em}\flushright #1}}}}


%% [optional] custom ampersand (font consistent with the one chosen above)
\newcommand{\amper}{{\fontspec[Scale=.95,Colour=AA0000]{Linux Libertine}\selectfont\&\,}}

%% No bullets on labels
\renewcommand{\labelitemi}{~}

%% Custom hanging indent for vita items
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
%\def\ind{\hangindent=18pt\hangafter=1 \noindent}
\def\labelitemi{~}
\renewcommand{\labelitemii}{~}

%%%------------------------------------------------------------------------
%%% Page layout
%%%------------------------------------------------------------------------

% These lines will insert git revision info in the footer, using the gitinfo
% package---see docs for gitinfo package for details. Comment out this line
% if you're not using git.
\pagestyle{kjh}
\thispagestyle{kjhgit}

%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------
\begin{minipage}[t]{2.95in}
 \flushright {\footnotesize
%%%%%%%%  UW details
 % \href{http://depts.washington.edu/anthweb/}{Department of Anthropology} \\ Box 353100 \\ University of Washington  \\ \vspace{-0.05in} Seattle \textsc{wa} 98195-3100}

%%%%%%%%  UOW details
 \href{http://cas.uow.edu.au/}{Centre for Archaeological Science}\\ University of Wollongong  \\ \vspace{-0.05in} \textsc{NSW} 2500}

\end{minipage}
\hfill
%\begin{minipage}[t]{0.0in}
% dummy (needed here)
%\end{minipage}
\hfill
\begin{minipage}[t]{1.7in}
  \flushright \footnotesize  \addressblock \myphone \, {\fontawesome\char"F095} \\
  {\scriptsize  \texttt{\href{http://twitter.com/benmarwick}{\mytwitter}} \, {\fontawesome\char"F099}  }\\
  {\scriptsize  \texttt{\href{mailto:\myemail}{\myemail}} \, {\fontawesome\char"F003}} \\
  %%{\scriptsize  \texttt{\href{\myweb}{\myweb}} \, {\fontawesome\char"F0AC}}
\end{minipage}

\medskip

%% Name
\noindent{\LARGE\scheader \textsc{bibliography}}
\reversemarginpar

\bigskip

% Bibliography: https://admin.artsci.washington.edu/promotion-and-tenure-documentation#curriculum

% The candidate's complete bibliography should be submitted, with entries listed in full bibliographic format, including range of page numbers or number of pages. In addition, the following items should be clearly indicated or distinguished:

% the type of each publication (article, book, review, monograph, technical report, etc.)
% the principal author(s) on multi-authored publications
% those publications which have had outside peer review before acceptance for publication
% a labeling of nonpublished material as "in press" or "accepted for publication," "submitted," or "work in progress" (note that "forthcoming" is ambiguous and should not be used)

\marginhead{\sffamily {{\vskip -0.35em} peer reviewed \newline journal articles}}

\ind \textbf{Marwick, B.}, & Birch, S. E. accepted, in press A Standard for the Scholarly Citation of Archaeological Data as an Incentive to Data Sharing.  \textit{Advances in Archaeological Practice} \href{https://osf.io/preprints/socarxiv/py4hz/}{preprint}  

\ind Schaarschmidt, M., Fu, X., Li, B., \textbf{Marwick, B.}, Khaing, K., Douka, K., & Roberts, R. G. 2018 pIRIR and IR-RF dating of archaeological deposits at Badahlin and Gu Myaung Caves–First luminescence ages for Myanmar. \textit{Quaternary Geochronology} DOI: https://doi.org/10.1016/j.quageo.2018.01.001

\ind \textbf{Marwick, B.}, Boettiger, C., & Mullen, L. 2017 \href{https://doi.org/10.1080/00031305.2017.1375986}{Packaging data analytical work reproducibly using R (and friends).} \textit{The American Statistician} DOI: https://doi.org/10.1080/00031305.2017.1375986 \href{https://doi.org/10.7287/peerj.preprints.3192v1}{preprint}

\ind  Clarkson, C., Jacobs, Z. \textbf{Marwick, B.}, and 19  others 2017 \href{http://dx.doi.org/10.1038/nature22968}{Human occupation of northern Australia by 65,000 years ago.} \textit{Nature} 547, pages 306–310 (20 July 2017) \href{https://doi.org/10.17605/OSF.IO/QWFCZ}{code & data}

\ind  \textbf{Marwick, B.}, P. Hiscock, M. Sullivan, P. Hughes 2017 \href{http://dx.doi.org/10.1016/j.jasrep.2017.07.004}{Landform boundary effects on Holocene forager landscape use in arid South Australia} \textit{Journal of Archaeological Science: Reports} DOI: http://dx.doi.org/10.1016/j.jasrep.2017.07.004 \href{https://doi.org/10.17605/OSF.IO/V2MS9}{preprint} \href{https://doi.org/10.17605/OSF.IO/EDZXS}{code & data}

\ind  \textbf{Marwick, B.}, E. Hayes, C. Clarkson, R. Fullagar 2017 {\href{https://doi.org/10.1016/j.jas.2017.01.008}{Movement of lithics by trampling: An experiment in the Madjedbebe sediments, northern Australia} \textit{Journal of Archaeological Science}  79: 73–85 \href{https://doi.org/10.17605/OSF.IO/V2MS9}{preprint} \href{https://doi.org/10.17605/OSF.IO/EDZXS}{code & data}

\ind \textbf{Marwick, B.} 2017 {\href{http://dx.doi.org/10.1007/s10816-015-9272-9}{Computational Reproducibility in Archaeological Research: Basic Principles and a Case Study of Their Implementation}. \textit{Journal of Archaeological Method and Theory} 24: 424. DOI: dx.doi.org/10.1007/s10816-015-9272-9.

\ind  Bulbeck, D., Aziz, F. A.,  O'Connor, S.,  Calo, A., Fenner, J. N., \textbf{Marwick, B.},  Feathers, J.,  Wood, R. \& Prastiningtyas, D. 2016. \href{http://dx.doi.org/10.1353/asi.2016.0017}{"Mortuary Caves and the Dammar Trade in the Towuti–Routa Region, Sulawesi, in an Island Southeast Asian Context."} \textit{Asian Perspectives} 55(2): 148-183.

\ind  \textbf{Marwick, B.}, Hannah Van Vlack; Cyler Conrad; Rasmi Shoocongdej; Cholawit Thongcharoenchaikit; Seungki Kwak 2016 \href{http://dx.doi.org/10.1016/j.jas.2016.10.010}{Adaptations to sea level change and transitions to agriculture at Khao Toh Chong rockshelter, Peninsula Thailand} \textit{Journal of Archaeological Science} 77: 94–108 \href{https://osf.io/preprints/socarxiv/axxf8/}{preprint} \href{https://dx.doi.org/10.6084/m9.figshare.2065602}{code & data}

\ind  \textbf{Marwick, B.}, Chris Clarkson; Sue O'Connor; Sophie Collins 2016 {\href{http://dx.doi.org/10.1016/j.jhevol.2016.09.004}{Early Modern Human Lithic Technology from Jerimalai, East Timor.} \textit{Journal of Human Evolution} 101: 45–64 \href{http://dx.doi.org/10.6084/m9.figshare.985406}{code & data}

\ind Steele, Teresa E., Alex Mackay, Kathryn E. Fitzsimmons,  \textbf{B. Marwick}, Jayson Orton, Steve Schwortz, Mareike C. Stahlschmidt 2016. Varsche Rivier 003:  {\href{http://www.paleoanthro.org/media/journal/content/PA20160100.pdf}{fA Middle Stone Age site with Still Bay and Howiesons Poort assemblages in southern Namaqualand, South Africa} \textit{PaleoAnthropology} 2016: 100−163. \href{https://github.com/benmarwick/Steele_et_al_VR003_MSA_Pigments}}{code & data}

\ind Conrad, C., Higham, C., Eda, M. and \textbf{B. Marwick} 2016 \href{https://doi.org/10.1353/asi.2016.0013}{Paleoecology and Forager Subsistence Strategies During the Pleistocene-Holocene Transition: A Reinvestigation of the Zooarchaeological Assemblage from Spirit Cave, Mae Hong Son Province, Thailand}. \textit{Asian Perspectives} 55(1): 2-27. \href{http://hdl.handle.net/1928/26730}{code & data}

\ind Tin Htut Aung, \textbf{B. Marwick}, C. Conrad 2015 \href{https://journals.lib.washington.edu/index.php/JIPA/article/view/14896}{Palaeolithic Zooarchaeology in Myanmar: A Review and Future Prospect} \textit{Journal of Indo-Pacific Archaeology} 39 DOI: 10.7152/jipa.v39i0.14896

\ind Kwak, S. and \textbf{B. Marwick} 2015 \href{http://journals.lib.washington.edu/index.php/JIPA/article/view/14708}{What did they cook? A preliminary investigation into culinary practices and pottery use in the central part of the Korean peninsula during the mid to late Holocene} \textit{Journal of Indo-Pacific Archaeology} 37  DOI: 10.7152/jipa.v37i0.14708

\ind Clarkson, C., Mike Smith, \textbf{B. Marwick}, Richard Fullagar, Lynley A. Wallis, Patrick Faulkner, Tiina Manne, Elspeth Hayes, Richard G. Roberts, Zenobia Jacobs, Xavier Carah, Kelsey M. Lowe, Jacqueline Matthews, S. Anna Florin 2015 \href{http://www.sciencedirect.com/science/article/pii/S0047248415000846}{The archaeology, chronology and stratigraphy of Madjedbebe (Malakunanja II): A site in northern Australia with early occupation} \textit{Journal of Human Evolution} 83: 46–64 DOI: 10.1016/j.jhevol.2015.03.014 \href{https://github.com/benmarwick/1989-excavation-report-Madjebebe}{code & data}

\ind Lowe, K., Wallis, L., Pardoe, C., \textbf{Marwick, B}., Clarkson, C., Manne, T., Smith, M. and R. Fullagar 2014 \href{http://faculty.washington.edu/bmarwick/PDFs/Lowe_et_al_2014_MJB_GPR.pdf}{Ground-penetrating radar and burial practices in western Arnhem Land}, Australia. \textit{Archaeology in Oceania} 49:148-157. DOI: 10.1002/arco.5039 \href{https://github.com/benmarwick/Rocks-and-burials-at-Madjebebe}{code & data}

\ind Mackay, A, T. Sumner, Z. Jacobs; \textbf{B. Marwick}, K. Bluff, M. Shaw. in press 2014.  \href{http://faculty.washington.edu/bmarwick/PDFs/Mackay_et_al_2014.pdf}{Putslaagte 1 (PL1), the Doring River, and the later Middle Stone Age in southern Africa's Winter Rainfall Zone}. \textit{Quaternary International} \newline DOI: 10.1016/j.quaint.2014.05.007 \href{https://github.com/benmarwick/Particle-size-analysis-Putslaagte-1}{code & data}

\ind \textbf{Marwick, B.} 2013. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2013_JAA.pdf}{Multiple Optima in Hoabinhian flaked stone artefact palaeoeconomics and palaeoecology at two archaeological sites in Northwest Thailand} \textit{Journal of Anthropological Archaeology} 34(2): 553–564. \href{http://dx.doi.org/10.6084/m9.figshare.765252}{code & data}

\ind Conrad, C., H. Van Vlack, \textbf{B. Marwick}, C. Thongcharoenchaikit, R. Shoocongdej, and B. Chaisuwan 2013 \href{http://faculty.washington.edu/bmarwick/PDFs/Conrad_et_al_2013_TNHMJ.pdf}{Summary of vertebrate and molluscan assemblages excavated from late-Pleistocene and Holocene deposits at Khao Toh Chong Rockshelter, Krabi, Thailand}. \textit{Thailand Natural History Museum Journal} 7(1): 11-22

\ind Brockwell, S., \textbf{B. Marwick}, P. Bourke, P. Faulkner and R. Willan. 2013. \href{http://faculty.washington.edu/bmarwick/PDFs/Brockwell_et_al_2013_AA.pdf}{Late Holocene Climate Change and Human Behavioural Variability in the Coastal Wet-Dry Tropics of Northern Australia: Evidence from a Pilot Study of Oxygen Isotopes in Molluscan Shells.} \textit{Australian Archaeology} 76: 21–33.

\ind Sullivan, M., T. Field, P. Hughes, \textbf{B. Marwick}, P. Przystupa, J. Feathers 2012. \href{http://faculty.washington.edu/bmarwick/PDFs/Sullivan_et_al_2012_OSL_dates_ODX.pdf}{OSL dates that inform late phases of dune formation and human occupation near Olympic Dam in northeastern South Australia.} \textit{Quaternary Australasia} 29(1): 4-11.

\ind Hughes, P., P. Hiscock, M. Sullivan and \textbf{B. Marwick}. 2011. \href{http://faculty.washington.edu/bmarwick/PDFs/Hughes_et_al_2011_JASSA.pdf}{An outline of archaeological investigations for the Olympic Dam Expansion in arid northeast South Australia}. \textit{Journal of the Anthropological Society of South Australia} 34:21-37

\ind \textbf{Marwick, B.} and M. Gagan 2011. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_and_Gagan_2011_QSR.pdf}{Late Pleistocene monsoon variability in northwest Thailand: an oxygen isotope sequence from the bivalve Margaritanopsis laosensis excavated in Mae Hong Son province.} \textit{Quaternary Science Reviews} 30(21-22): 3088-3098

\ind \textbf{Marwick, B.} 2010. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2010_WA_Wall-E.pdf}{Self-image, the long view and archaeological engagement with film: An animated case study.} \textit{World Archaeology} 42(3): 394–404

\ind \textbf{Marwick, B.} 2009a. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2009_AO_Pilbara.pdf}{Change or Decay? An interpretation of late Holocene archaeological evidence from the Hamersley Plateau, Western Australia.} \textit{Archaeology in Oceania} 44: 16-22

\ind \textbf{Marwick, B.}  2009b. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2009_QI.pdf}{Biogeography of Middle Pleistocene Hominins in Mainland Southeast Asia: A Review of Current Evidence.} \textit{Quaternary International} 202: 51–58

\ind \textbf{Marwick, B.} 2008a. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2008_Before_Farming.pdf}{Stone artefacts and recent research in the archaeology of mainland Southeast Asian hunter-gatherers.} \textit{Before Farming} 2008/4

\ind \textbf{Marwick, B.} 2008b. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2008_AA_3_Styles.pdf}{Three Styles of Darwinian Evolution in the Analysis of Stone Artefacts: Which one to use in Mainland Southeast Asia?} \textit{Australian Archaeology} 67: 79-86

\ind \textbf{Marwick, B.} 2008c. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2008_BIPPA.pdf}{Beyond typologies: The reduction thesis and its implications for lithic assemblages in Southeast Asia.} \textit{Bulletin of the Indo-Pacific Prehistory Association} 28: 108-116

\ind \textbf{Marwick, B.} 2008d. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2008_JAS.pdf}{Identifying variation in Hoabinhian lithic technology: An index of flake cortex distribution for the measurement of cobble reduction intensity.} \textit{ Journal of Archaeological Science} 35(5): 1189-1200.

\ind \textbf{Marwick, B.} 2007. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2007_SIJ.pdf}{Approaches to Stone Artefact Archaeology in Thailand: A Historical Review.} \textit{Silpakorn University International Journal} 7:49-88

\ind \textbf{Marwick, B.} 2005a. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2005_LHE.pdf}{The interpersonal origins of language: Social and linguistic implications of an archaeological approach to language evolution.} \textit{Linguistics and the Human Sciences} 1.2: 197-224.

\ind \textbf{Marwick, B.} 2005b. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2005_JAS.pdf}{Element Concentrations and Magnetic Susceptibility of Anthrosols: Indicators of Prehistoric Human Occupation in the inland Pilbara, Western Australia.} \textit{Journal of Archaeological Science} 32: 1357-1368.

\ind \textbf{Marwick, B.} 2003. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2003_CAJ.pdf}{Pleistocene exchange networks as evidence for the evolution of language.} \textit{Cambridge Archaeological Journa}l 17(1):67-81.

\ind \textbf{Marwick, B.} 2002a. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2002_Tempus.pdf}{Milly’s Cave: Evidence for Human Occupation of the Inland Pilbara during the Last Glacial Maximum.} \textit{Tempus} 21-33.

\ind \textbf{Marwick, B.} 2002b. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2002_RWAM.pdf}{Evidence of Prehistoric Occupation of the Abrolhos Islands, Western Australia.} \textit{Records of the Western Australian Museum} 20(4):461-464.

\bigskip

\marginhead{\sffamily {{\vskip -0.35em} peer reviewed \newline book chapters}}

\ind Bulbeck, D. and \textbf{B. Marwick}. accepted, in press. Stone Industries of Mainland and Island Southeast Asia. In Nam Kim and Charles Higham (eds) \textit{Handbook of Southeast Asian Archaeology.} Oxford University Press.

\ind \textbf{Marwick, B.} 2018. The Hoabinhian of Southeast Asia and its Relationship to Regional Pleistocene Lithic Technologies. In Erick Robinson and Frédéric Sellet (eds) \textit{Lithic Technological Organization and Paleoenvironmental Change: Global and Diachronic Perspectives}. Springer. \href{https://doi.org/10.17605/OSF.IO/9PT8G}{preprint}

\ind \textbf{Marwick, B.} and B. Bouasisengpaseuth accepted, in press. The history and practice of archaeology in Laos. In Junko Habu, Peter Lape, John Olsen  and Jing Zhichun (eds) \textit{ Handbook of East and Southeast Asian Archaeology.} Springer. \href{https://dx.doi.org/10.17605/OSF.IO/75ZHC}{preprint}

\ind Rokem, A. \textbf{B. Marwick}, and V. Staneva 2017 \href{https://www.practicereproducibleresearch.org/core-chapters/2-assessment.html}{Assessing Reproducibility.} In Justin Kitzes, Daniel Turek, Fatma Deniz (eds) \textit{The Practice of Reproducible Research: Case Studies and Lessons from the Data-Intensive Sciences.} University of California Press.

\ind Ram, K. and \textbf{B. Marwick} 2017 \href{https://www.practicereproducibleresearch.org/core-chapters/6-future.html}{Building Towards a Future Where Reproducible, Open Science is the Norm.} In Justin Kitzes, Daniel Turek, Fatma Deniz (eds) \textit{The Practice of Reproducible Research: Case Studies and Lessons from the Data-Intensive Sciences.} University of California Press.

\ind \textbf{Marwick, B.} 2017 \href{https://www.practicereproducibleresearch.org/case-studies/benmarwick.html}{Using R and Related Tools for Reproducible Research in Archaeology.} In Justin Kitzes, Daniel Turek, Fatma Deniz (eds) \textit{The Practice of Reproducible Research: Case Studies and Lessons from the Data-Intensive Sciences.} University of California Press. 

\ind Kretzler, I. and \textbf{B. Marwick} 2015 \href{http://faculty.washington.edu/bmarwick/PDFs/Kretzler_Marwick_2014_Chacmool.pdf}{Investigating Archaeologists' Engagement With Feminist Theory Using Textual Macroanalysis: 25 Years after Chacmool 1989}. \textit{Breaking barriers: Proceedings of the 47th Annual Chacmool Archaeological Conference November 7-9, 2014 Calgary, Alberta, Canada}. Robyn Crook, Kim Edwards and Colleen Hughes (eds). The University of Calgary, Chacmool Archaeological Association. pp. 158-168

\ind \textbf{Marwick, B.} 2013. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2013_DMAR.pdf}{Text mining and topic modeling for discovery of current issues in Anthropology using microblog content.} In  Yanchang Zhao and Yonghua Cen (eds) \textit{Data Mining Applications with R.} Elsevier. p. 63-93.

\ind \textbf{Marwick, B.}, R. Shoocongdej, C. Thongcharoenchaikit, B. Chaisuwan, C. Khowkhiew and S. Kwak.  2013. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_et_al_2013_community.pdf}{Hierarchies of engagement and understanding: Community engagement during archaeological excavations at Khao Toh Chong rockshelter, Krabi, Thailand.} In O’Connor, S (ed.) \textit{Transcending the Culture-Nature Divide in Cultural Heritage: Views from the Asia-Pacific Region}. Terra Australis, ANU E Press.

\ind \textbf{Marwick, B.} 2012. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2012_Buddha_cladistics.pdf}{Transmission of craft traditions in bronze Buddha manufacturing in ancient Thailand: A pilot study of the Griswold collection using cladistic techniques.} In Dominik Bonatz, Andreas Reinecke, Mai Lin Tjoa-Bonatz (eds.)\textit{ Connecting Empires and States: Selected Papers from the 13th Conference of the European Association of Southeast Asian Archaeologists.} National University of Singapore Press, Singapore. pp. 161-178.

\ind Mackay, A. and \textbf{B. Marwick} 2011. \href{http://faculty.washington.edu/bmarwick/PDFs/Mackay_and_Marwick_2011_timecost.pdf}{Costs and benefits in technological decision making under variable conditions: examples from the late Pleistocene in southern Africa.} In \textbf{B. Marwick} and A. Mackay (eds.) \textit{Keeping Your Edge: Recent Approaches to the Organisation of Stone Artefact Technology}. British Archaeological Reports.  pp. 119-134

\ind \textbf{Marwick, B.} 2008. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2008_EurASEAA.pdf}{Human Behavioural Ecology and Stone Artefacts in Northwest Thailand during the Terminal Pleistocene and Holocene.} Jean-Pierre Pautreau (ed) \textit{Southeast Asian Prehistory: The 11th EurASEAA}. Musée de Bougon: Paris. pp. 37-49.

\bigskip

\marginhead{\sffamily {{\vskip -0.35em} book reviews \newline (no outside \newline peer review)}}

\ind \textbf{Marwick, B.} 2015a. \href{https://www.academia.edu/15214960/Review_of_Geoarchaeology_of_Aboriginal_Landscapes_in_Semi-Arid_Australia._Simon_J._Holdaway_and_Patricia_C._Fanning._2014._CSIRO_Collingwood._Geoarchaeology_Article_first_published_online_26_AUG_2015_DOI_10.1002_gea.21522}{Review of "Geoarchaeology of Aboriginal Landscapes in Semi-Arid Australia." Simon J. Holdaway and Patricia C. Fanning. 2014. CSIRO, Collingwood} \textit{Geoarchaeology}  DOI: 10.1002/gea.21522

\ind \textbf{Marwick, B.} 2015b. \href{http://intarch.ac.uk/journal/issue39/3/comms.cfm#tabs-3}{Films, digs and death: a review of the Project Eliseg video} \textit{Internet Archaeology} DOI: http://dx.doi.org/10.11141/ia.39.3.com3

\ind \textbf{Marwick, B.} 2009a. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2009_AA_Stark_Review.pdf}{Review of “Cultural Transmission and Material Culture: Breaking Down Boundaries.” Miriam Stark, Brenda Bowser and Lee Horne, eds. Tucson: University of Arizona Press, 2008.} \textit{American Anthropologist} 111(4): 540-541

\ind \textbf{Marwick, B.} 2009b. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2009_Shiner_review.pdf}{Review of "Place as Occupational Histories: An Investigation of the Deflated Surface Archaeological Record of Pine Point and Langwell Stations, Western New South Wales, Australia." by Justin Shiner. Archaeopress, Oxford, (2008).} \textit{Australian Archaeology} 69: 82

\ind \textbf{Marwick, B.} 2007. \href{http://faculty.washington.edu/bmarwick/PDFs/Evolution.pdf}{Review of “The origins and evolution of cultures”, by Peter Richerson and Robert Boyd. Oxford University Press, London, (2004).} \textit{The Australian Journal of Anthropology} 18(1): 97-98.

\ind \textbf{Marwick, B.} 2006. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2006_[B&R].pdf}{What can archaeology do with Boyd and Richerson’s Co-evolutionary program? Review of “Not By Genes Alone”, by Peter Richerson and Robert Boyd. Chicago University Press, Chicago, (2005)}. \textit{The Review of Archaeology} 26(2): 30-40.

\ind \textbf{Marwick, B.} 2005a. \href{http://faculty.washington.edu/bmarwick/PDFs/Uncovered.pdf}{Review of “Agency uncovered: Archaeological perspectives on social agency, power, and being human, edited by Andrew Gardner. UCL Press, London, (2004).} \textit{Anthropological Forum} 15(2): 203-204.

\ind \textbf{Marwick, B.} 2005b. \href{http://faculty.washington.edu/bmarwick/PDFs/Ghosts.pdf}{Review of “Marx’s ghost: Conversations with archaeologists”, by Thomas C. Patterson. Berg, Oxford. (2003)}. \textit{Anthropological Forum} 15(1): 92-94

\ind \textbf{Marwick, B.} 2003. \href{http://faculty.washington.edu/bmarwick/PDFs/Batavia.pdf}{Review of “Batavia’s graveyard. The true story of the mad heretic who lead history’s bloodiest mutiny”, by Mike Dash.} London: Weidenfeld and Nicolson. (2002). \textit{Limina} vol. 9: 236-240.

\ind \textbf{Marwick, B.} 2002. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2002_Dictionary.pdf}{Review of “A dictionary of archaeology”, edited by Ian Shaw and Robert Jameson. Oxford: Blackwell Publishers Ltd. (2002)} \textit{Australian Archaeology} 55: 50-51

\bigskip

\newpage

\marginhead{\sffamily {{\vskip -0.35em} editor-reviewed \newline publications \newline (no outside \newline peer review)}}

\ind \textbf{Marwick, B.}, d’Alpoim Guedes, J., Barton, C. M., Bates, L. A., Baxter, M., Bevan, A., Bollwerk, E. A., Bocinsky, R. K., Brughmans, T., Carter, A. K., Conrad, C., Contreras, D. A., Costa, S., Crema, E. R., Daggett, A., Davies, B., Drake, B. L., Dye, T. S., France, P., Fullagar, R., Giusti, D., Graham, S., Harris, M. D., Hawks, J., Health, S., Huffer, D., Kansa, E. C., Kansa, S. W., Madsen, M. E., Melcher, J., Negre, J., Neiman, F. D., Opitz, R., Orton, D. C., Przstupa, P., Raviele, M., Riel-Savatore, J., Riris, P., Romanowska, I., Smith, J., Strupler, N., Ullah, I. I., Van Vlack, H. G., VanValkenburgh, N., Watrall, E. C., Webster, C., Wells, J., Winters, J., and Wren, C. D. (2017) \href{Open science in archaeology}{http://www.saa.org/Portals/0/SAA_Record_Sept_2017_Final_LR.pdf#page=10}. \textit{SAA Archaeological Record}, 17(4), pp. 8-14. 

\ind Eglen, S. J., \textbf{B. Marwick}, Y. O. Halchenko, M. Hanke, S. Sufi, P. Gleeson, R. A. Silver, A. P. Davison, L. Lanyon, M. Abrams, T. Wachtler, D. J. Willshaw, C. Pouzat and J.-B. Poline (2017). \href{http://www.nature.com/neuro/journal/v20/n6/full/nn.4550.html}{Toward standard practices for sharing computer code and programs in neuroscience.} \textit{Nature Neuroscience} 20(6): 770-773.

\ind \textbf{Marwick, B.} 2016 \href{https://theconversation.com/how-computers-broke-science-and-what-we-can-do-to-fix-it-49938}{How computers broke science - and what we can do to fix it}. \textit{The Conversation} 15 Nov 2015.  Syndicated on \href{http://gizmodo.com/how-computers-broke-science-and-what-we-can-do-to-fix-i-1741649207}{Gizmodo}, \href{http://www.geekwire.com/2015/how-computers-broke-science-and-what-we-can-do-to-fix-it/}{Geekwire}, \href{http://qz.com/548730/computers-are-making-science-extremely-challenging-for-scientists/}{Quartz}, \href{http://www.netzpiloten.de/wissenschaft-computer-reproduzierbarkeit-probleme/}{Netzpiloten (in German)}, \href{http://filled-with-deities.hatenablog.jp/entry/2015/11/17/202013}{書は人間の夢を見るか (in Japanese)}, and \href{https://theconversation.com/les-ordinateurs-nuisent-gravement-a-la-science-mais-il-est-possible-dy-remedier-1-52024}{The Conversation (in French)}.

\ind \textbf{Marwick, B.} and A. Mackay 2011. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_and_Mackay_2011_intro.pdf}{Keeping your edge: Recent approaches to the organisation of stone artefact technology.} In \textbf{B. Marwick} and A. Mackay (eds.) \textit{Keeping Your Edge: Recent Approaches to the Organisation of Stone Artefact Technology}. British Archaeological Reports.  pp. 1-4.

\ind White, J.C., Lewis, H., Bouasisengpaseuth, B., \textbf{Marwick, B.} and K. Arrell 2009. \href{http://faculty.washington.edu/bmarwick/PDFs/White_et_al_2009_Antiquity.pdf}{Archaeological investigations in northern Laos: New contributions to Southeast Asian prehistory.} \textit{Antiquity} 83(319) Project Gallery

\ind \textbf{Marwick, B.}, White, J.C., B. Bouasisengpaseuth 2009. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_et_al_2009_MMAP.pdf}{The Middle Mekong Archaeology Project and International Collaboration in Luang Prabang, Laos.} \textit{SAA Archaeological Record} 9 (3) 25-27

\ind \textbf{Marwick, B.} 2006. A Methodological Study of Technological Attributes in Hoabinhian Lithic Assemblages. In R. Shoocondej (ed.)  \textit{Social, Cultural and Environmental Dynamics in the Highlands of Pangmapha, Mae Hong Son Province: Integrated Archaeological Research into the Region}. Highland Archaeology Project in Pangmapha: Bangkok. pp. 231-244.

\ind \textbf{Marwick, B.} 2004. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2004_AACAI.pdf}{Future directions for research into open sites and rockshelters in the inland Pilbara.} \textit{Australian Association of Consulting Archaeologists Inc. Newsletter} 95:14-18.


\end{document}
