%%% A template to produce a nice-looking Curriculum Vitae.
%%% Originally from Kieran Healy <kjhealy@gmail.com>
%%% Kieran's source is at http://kjhealy.github.com/kjh-vita
%%%
%%% This source code has been adapted by 
%%% Ben Marwick <benmarwick@gmail.com> and is largely
%%% determined by the instructions here:
%%% https://admin.artsci.washington.edu/promotion-and-tenure-documentation#curriculum
%%%
%%% questions: where to put on campus presentation on scholarly and teaching topics?
%%% ------------------------------------------------------------------------
%%% Requirements for this docuemnt that are included
%%%  in (or otherwise easily obtained) a modern tex distribution:
%%% ------------------------------------------------------------------------
%%% xelatex (I'm using MiKTeX & Texmaker)
%%% fontspec.sty
%%% hyperrref.sty
%%% xunicode.sty
%%% color.sty
%%% url.sty
%%% fancyhdr.sty
%%% memoir.cls
%%% fontawesome.sty
%%% gitinfo.sty
%%% 
%%% 
%%% ------------------------------------------------------------------------
%%% Requirements from https://github.com/kjhealy/latex-custom-kjh
%%% ------------------------------------------------------------------------
%%% org-preamble-xelatex.sty
%%% memoir-article-styles.sty
%%%
%%% 
%%% ------------------------------------------------------------------------
%%% Note
%%%------------------------------------------------------------------------
%%% Because this is a hand-tweaked file, be on the look out for \medksip, 
%%% \bigskip and \newpage commands here and there, which are used to balance
%%% the layout or avoid widows & orphans, etc. You should of course add or 
%%% remove these as needed.
%%%------------------------------------------------------------------------

\documentclass[11pt,article,oneside]{memoir}   
\usepackage{org-preamble-xelatex} 
\usepackage{fontawesome,url}
\usepackage{setspace}
\usepackage[footinfo]{gitinfo}


%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------

%% Change as needed.
\def\myauthor{Ben Marwick}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myaffiliation{University of Washington}
\def\myaddress{Anthropology Department}
\def\myemail{bmarwick@uw.edu}
\def\myweb{http://faculty.washington.edu/bmarwick/ }
\def\myphone{(206) 552-9450}
\def\myfax{(206) 543-3285}
\def\mytwitter{@benmarwick}
\def\myversion{}
\def\myrevision{}


\def\myaffiliation{University of Washington}
\def\myauthor{Ben Marwick}
\date{} % not used (revision control instead)
\def\mykeywords{}


%%%------------------------------------------------------------------------
%%% Document
%%%------------------------------------------------------------------------
\begin{document}

%% Choose fonts for use with xelatex
%% Using free fonts with big glyph sets for maximum flexibility  
%% http://www.linuxlibertine.org/index.php?id=2&L=1
%% http://font.ubuntu.com/

\setromanfont[Mapping={tex-text}, 
	Numbers={OldStyle},
	Ligatures={Common}]{Linux Libertine}
\setsansfont[Mapping=tex-text,
	Ligatures={Common}, 
	Colour=AA0000]{Linux Biolinum}
\setmonofont[Mapping=tex-text,Scale=0.72]{Ubuntu} 

\newfontface\scheader[SmallCapsFont={Linux Libertine},SmallCapsFeatures={Letters=SmallCaps}]{Linux Libertine}

\newfontface\addressblock[Mapping={tex-text}, 
	Numbers={OldStyle},
	Ligatures={Common}]{Linux Libertine}


%%%------------------------------------------------------------------------
%%% Local commands
%%%------------------------------------------------------------------------

%% Marginal header
%% Note: as the document goes on you may need to introduce a (gradually increasing)
%% \vspace element to keep the marginal header pleasingly aligned with the first 
%% item in the body text. Like this: \marginhead{{\vskip 0.4em}Grants}, or 
%% \marginhead{{\vskip 0.8em}Service}. Experiment as needed.
\newcommand{\marginhead}[1]{\marginpar{\textsf{{\footnotesize\vspace{-1em}\flushright #1}}}}


%% [optional] custom ampersand (font consistent with the one chosen above)
\newcommand{\amper}{{\fontspec[Scale=.95,Colour=AA0000]{Linux Libertine}\selectfont\&\,}}

%% No bullets on labels
\renewcommand{\labelitemi}{~} 

%% Custom hanging indent for vita items
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
%\def\ind{\hangindent=18pt\hangafter=1 \noindent}
\def\labelitemi{~}
\renewcommand{\labelitemii}{~}

%%%------------------------------------------------------------------------
%%% Page layout
%%%------------------------------------------------------------------------

% These lines will insert git revision info in the footer, using the gitinfo
% package---see docs for gitinfo package for details. Comment out this line
% if you're not using git.
\pagestyle{kjh}
\thispagestyle{kjhgit}

%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------
\begin{minipage}[t]{2.95in}
 \flushright {\footnotesize 
 \href{http://depts.washington.edu/anthweb/}{Department of Anthropology} \\ Box 353100 \\ University of Washington  \\ \vspace{-0.05in} Seattle \textsc{wa} 98195-3100}  
  
\end{minipage}
\hfill     
%\begin{minipage}[t]{0.0in}
% dummy (needed here)
%\end{minipage}
\hfill
\begin{minipage}[t]{1.7in}
  \flushright \footnotesize  \addressblock \myphone \, \faPhone \\ 
  {\scriptsize  \texttt{\href{http://twitter.com/benmarwick}{\mytwitter}} \, \faTwitter }  \\ 
  {\scriptsize  \texttt{\href{mailto:\myemail}{\myemail}} \, \faEnvelope} \\
  {\scriptsize  \texttt{\href{\myweb}{\myweb}} \, \faGlobe}
\end{minipage}

\medskip

%% Name 
\noindent{\LARGE\scheader \textsc{ben marwick}}
\reversemarginpar

\bigskip       

%% Appointments

\marginhead{\sffamily employment}

\ind Assistant Professor in Archaeology,  University of Washington, 2011--Present.   

\ind Post-Doctoral Fellow, ACLS/Luce Foundation,  University of Washington, 2010-11.      

\ind Assistant Professor in Archaeology,  University of Washington, 2008--2010.    

\ind Consultant Archaeologist, Huonbrook Environment and Heritage, South Australia, 2006--2008.

\ind Research Associate, Society, State and Governance in Melanesia Project and The Pacific Centre, Research School of Pacific and Asian Studies, The Australian National University, 2006--2008.

\bigskip

%% Education

\marginhead{\sffamily {{\vskip -0.35em} education}}

\ind Ph.D, Archaeology and Natural History, Australian National University, 2008.

 \vspace{0.05in}
\begin{Spacing}{0.75}
\ind \hspace{0.35in} 
\footnotesize {Dissertation: \emph{\href{http://dx.doi.org/10.6084/m9.figshare.765252}{Stone artefacts and human ecology at two rockshelters in Northwest Thailand}}} \normalsize \vspace{0.05in}
 \end{Spacing}

\ind M.A., Archaeology, University of Western Australia, 2002. 

\vspace{0.05in}
\begin{Spacing}{0.75} 
\ind \hspace{0.35in} \footnotesize Dissertation: \emph{\href{http://dx.doi.org/10.6084/m9.figshare.765251}{ Inland Pilbara Archaeology: A Study of Variation in Aboriginal Occupation over Time and Space on the Hamersley Plateau}} \normalsize \vspace{0.05in}
 \end{Spacing}

\ind B.A. (Hons.), First Class, University of Western Australia, 1999.

\bigskip

%% Research projects, grants, contracts

\marginhead{\sffamily {{\vskip 0.1em} research projects  \newline \& grants}}
\medskip

\ind  Deutscher Akademischer Austausch Dienst, Research Visit Travel Grant (2014, sole PI, TDC USD 6,000)

\ind  ``Micromorphology at key archaeological sites at the end of the arc of modern human dispersal", UW Royalty Research Fund, (2014, sole PI, TDC USD 31,005)

\ind  Marwick, B and S. Kwak. ``Long-term chronology of subsistence and the role of intensive rice agriculture in the central part of the prehistoric Korean peninsula", National Science Foundation Doctoral Dissertation Research Improvement Grant, (2013,  PI with graduate student, TDC USD 23,373)

\ind  Roberts, R., Mokhtar Saidin, Ben Marwick, Dong Truong Nguyen, Nigel Spooner, Regina DeWitt, Anatoly Rosenfeld, Zenobia Jacobs, Bo Li, Susanna Guatelli, C. Clarkson, Adam Brumm and Kat Szabó ``Out of Asia: unique insights into human evolution and interactions using frontier technologies in archaeological science".  Australian Research Council (2013, TDC AUD 
3,182,338)

\ind Lewis, H. and B. Marwick,  University College Dublin Seed Funding. University College Dublin (July 2012, Co-PI, TDC EUR 5,200.00) 

\ind Vice Provost’s International Faculty Exchange Grant (2012, PI, TDC USD 3500)

\ind  ``Investigating modern human origins and early behavioural complexity in Australia", UW Office of Research Trans-Pacific Early Career Academic Fellowship (2011, sole PI, TDC USD 13,125)

\ind UW Office of Global Affairs Herbert H. Gowen International Studies Award (2011, sole PI, TDC USD 2,500)

\ind O’Connor. S., J. Fenner, J. Stevenson, K. Dobney, B. Marwick, E. St Pierre and G. Larson ``The Archaeology of Sulawesi: A Strategic Island for Understanding Modern Human Colonization and Interactions Across our Region", Australian Research Council (March 2010, Co-PI, TDC AUD 1,757,919)

\ind Clarkson, C., B. Marwick, L. Wallis, M. Smith and R. Fullgar  ``Modern Human Origins and Early Behavioural Complexity in Australia and South East Asia", Australian Research Council (March 2010). (Co-PI, TDC AUD 1,189,790)

\ind UW Centre for Statistics in the Social Sciences Undergraduate Research Grant (2010, sole PI, TDC USD 4,480)

\ind American Council  of Learned Societies/Luce Foundation Postdoctoral Fellowship (2010-2011, sole PI, TDC USD 36,000)

\ind UW Office of Global Affairs Herbert H. Gowen International Studies Award (2010,sole  PI, TDC USD 5,000)

\ind UW Centre for Statistics in the Social Sciences Seed Grant (2009,sole PI, TDC USD 18,347)

\ind Dorothy Cameron Prize for best archaeological publication at The Australian National University (2008, AUD 500)

\ind Postgraduate Research Grant, Australian Institute of Nuclear Science and Technology (2007, sole PI, TDC AUD 5,000)

\bigskip

%% Invited talks

\marginhead{\sffamily {\vskip 0.3em} invited \newline scholarly talks}

\medskip

\ind Marwick, B. 2014. ``Palaeolithic archaeology in mainland Southeast Asia". Department of Archaeology, University of Yangon, Myanmar. Jan 19, 2014. Invited Presentation.

\ind Marwick, B. 2013. ``Research Report on Middle Holocene Research in mainland Southeast Asia". Southeast Asia Archaeology Workshop, University of Hawaii-Manoa, April 2013. Invited Presentation.

\ind Marwick, B. 2013 ``The Hoabinhian of Southeast Asia and its relationship to global Pleistocene lithic technologies". International Symposium on the Palaeolithic Cultures in Taiwan and Its Surrounding Areas, Academia Sinica, Taitung, Taiwan, 29-31 March 2013.  Invited Presentation.

\ind Marwick, B. 2013 ``Pleistocene lithic technologies in Mainland Southeast Asia: How does the Hoabinhian fit in?"  International Conference on Recent Advances in the Archaeology of East and Southeast Asia. University of Wisconsin-Madison, Wisconsin, USA, March 15-16, 2013. Invited Presentation.

\ind Marwick, B. 2012 ``Cultural Phylogenetics of Religion using Thai and Lao Bronze Buddha Statues". Department of Archaeology, University College Dublin, Ireland. Nov 22, 2012. Invited Presentation.

\ind Marwick, B. 2009 ``Pleistocene Exchange Networks as Evidence of Language Evolution".  UBC/SFU Human Evolution, Culture and Cognition seminar series, UBC, Vancouver, Canada. Invited presentation

\bigskip

%% Talks and presentations

\marginhead{\sffamily {\vskip 0.3em} contributed \newline scholarly \newline talks \& \newline presentations \newline (since 2008)}

\medskip

\ind Sonethongkham, S. and B. Marwick 2014 ``Variation in cores excavated from four rockshelter sites in Luang Prabang Province, Lao PDR". Peer-reviewed presentation at the Indo-Pacific Prehistory Association conference, Jan 2014, Siam Reap.

\ind Marwick, B.  and S. Sonethongkham 2014 ``Patterns in Holocene flaked artefact technology from excavations in Luang Prabang Province, Lao PDR" . Peer-reviewed presentation at the Indo-Pacific Prehistory Association conference, Jan 2014, Siam Reap.

\ind Marwick, B. C. Clarkson, S. O’Connor and S. Collins 2014 ``Pleistocene lithic technology from East Timor: remarkable long term stability in technological behaviours" . Peer-reviewed presentation at the Indo-Pacific Prehistory Association conference, Jan 2014, Siam Reap.

\ind Hayes, E., R. Fullagar, C. Clarkson, M. Smith and B. Marwick 2014 ``Pleistocene evidence for seed grinding in Australia". Peer-reviewed presentation at the Indo-Pacific Prehistory Association conference, Jan 2014, Siam Reap.

\ind Clarkson, C., M. Smith, B. Marwick, R. Fullagar, T. Manne, K. Lowe, X. Carah,  A. Florin, A.  Fairbairn, C. Pardoe and L. Wallis 2014 ``Excavations at Malakunanja II, northern Australia" ,  Peer-reviewed presentation at the Indo-Pacific Prehistory Association conference, Jan 2014, Siam Reap.

\ind Clarkson, C., M. Smith, R. Fullagar, B. Marwick, T. Manne, L. Wallis, Z. Jacobs, R. Roberts, K. Lowe, A. Florin, X. Carah, C. Pardoe and E. Hayes 2013 ``Report on new research at Madgedbebe (Malakunanja II)" . Peer-reviewed presentation at the Australian Archaeological Association Annual Conference, Dec 2013, Coff’s Harbour. 

\ind Wallis, L., C. Pardoe, T. Manne, K. M. Lowe, J. Matthews, C.   Clarkson, B. Marwick, R. Fullagar and M. Smith 2013 ``Much more than just an old site: Human remains from the 2012 excavations at Madjedbebe, western Arnhem Land, Australia" . Peer-reviewed presentation at the Australian Archaeological Association Annual Conference, Dec 2013, Coff’s Harbour.

\ind Lowe, K. L. A. Wallis, C. Pardoe, B. Marwick C. Clarkson, T. Manne, M. Smith and R. Fullagar. 2013 ``Ground-penetrating radar, GIS and burial practices in western Arnhem Land, Australia". Peer-reviewed presentation at the Australian Archaeological Association Annual Conference, Dec 2013, Coff’s Harbour.

\ind Hayes, E.  R. Fullagar, C. Clarkson, B. Marwick, M. Smith, L. Wallis and T. Manne, 2013 ``Pleistocene evidence for seed grinding in Australia". Peer-reviewed presentation at the Australian Archaeological Association Annual Conference, Dec 2013, Coff’s Harbour.

\ind Florin, A., C. Clarkson, A. Fairbairn, R. Fullagar, B. Marwick, L. Wallis, X. Carah, T. Manne and M. Smith. 2013 ``Archaeobotanical investigations into plant food use at Madjedbebe (Malakunanja II)". Peer-reviewed presentation at the Australian Archaeological Association Annual Conference, Dec 2013, Coff’s Harbour.

\ind Marwick, B. E. Hayes and C. Clarkson 2013 ``Movement of lithics by trampling: An experiment in the Malakunanja II sediments". Peer-reviewed poster at the Society of American Archaeology Annual Meeting, April 3-7, Honolulu, Hawaii. 2013

\ind Macy, K., B. Marwick, B. S. Hanyu, C. Conrad and A. Mackay 2013 ``Where did the dirt come from? Geochemical sediment tracing at Klipfonteinrand rockshelter, western South Africa". Peer-reviewed poster at the Society of American Archaeology Annual Meeting, April 3-7, Honolulu, Hawaii. 2013

\ind Bulbeck, D., B. Marwick, S. O'Connor, F. Aziz, A. Calo, J. Fenner, B. Hakim, A. Oktaviana and E. St Pierre 2013 ``Archaeology of Lake Towuti: Survey and Excavation in South Sulawesi". Peer-reviewed poster at the Society of American Archaeology Annual Meeting, April 3-7, Honolulu, Hawaii. 2013

\ind Marwick, B., P. Hiscock, P. Hughes and M. Sullivan. 2013 ``The use of mobile Geographic Information Systems for intensive archaeological survey in arid northeastern South Australia". Peer-reviewed presentation at the Computer Applications and Quantitative Methods in Archaeology Conference, University of Western Australia, Perth, Australia, March 18-21, 2013

\ind Marwick, B. ``How archaeologists explain (and how they ought to): Theory and practice of explanation in Australian archaeology". Peer-reviewed presentation at the Australian Archaeological Association, Wollongong, Australia, Dec 2012.

\ind Marwick, B, Anna Cohen, S. Kwak, K. Macy and A. Cowan 2011 ``Geoarchaeology of Iron Age ceramics at Tham Sua Cave, Northern Lao PDR". Peer-reviewed poster at the Society of American Archaeology Annual Meeting, Sacramento, CA.

\ind Marwick, B, T. Field, J. Martinez, P. Przystupa, K. Abbott, K. Macy, L. Minchk, P. Hughes and M. Sullivan 2010. ``Landscape archaeology in arid northeast South Australia: Preliminary investigations into relationships between site distributions, surface geology, water sources and wind patterns". Peer-reviewed poster at the Australian Association of Archaeology Annual Conference, Bateman’s Bay, New South Wales.

\ind Marwick, B, S. O’Connor and S. Collins 2010. ``Pleistocene-aged stone artefacts from Jerimalai, East Timor: Early modern human technology in island Southeast Asia". Peer-reviewed presentation at the 13th International Conference of the European Association of Southeast Asian Archaeologists (EurASEAA), Berlin, Germany.

\ind Marwick, B and Vanpheng Keopanna 2010. ``A pilot study of Geometric morphometric analysis of bronze Buddha craft traditions in the Lao PDR". Peer-reviewed presentation  at the 13th International Conference of the European Association of Southeast Asian Archaeologists (EurASEAA), Berlin, Germany.

\ind Marwick, B, 2010. ``Do Model-based explanations suit archaeology better than Inference to the Best Explanation?" Peer-reviewed presentation at the Society of American Archaeology Annual Meeting, St Louis, MO.

\ind Marwick, B, Ariel Auerbach and A. Cowan 2009. ``Geoarchaeology at Tham Sua Cave, Luang Prabang Province, Lao PDR". Peer-reviewed presentation at the Indo-Pacific Prehistory Association Congress, Hanoi, Vietnam.

\ind Brockwell, S., B. Marwick, P. Bourke, P. Faulkner, R. Willan 2009. ``Climate change records from North Australian cultural midden deposits: evidence from a pilot study of oxygen isotopes in mollusc shells". Peer-reviewed presentation  at the Australian Archaeological Association Annual Conference, Flinders University, Adelaide, South Australia.

\ind Brockwell, S.. P. Bourke, P. Faulkner, B. Marwick, B. Meehan. 2008. ``Climate Change and Behavioural Variability in Coastal Northern Australia". Peer-reviewed presentation at the World Archaeological Congress, Dublin,  Jul 2008. 

\ind Marwick, B. P. Hughes, P Hiscock, M. Sullivan, O. Macgregor 2008. ``Mobile Geographic Information Systems for Large-scale Intensive Archaeological Survey of Stone Artefact Scatters in Arid Australia". Peer-reviewed presentation at the Australian Archaeological Association Annual Conference, Noosa Dec 3-6 2008

\ind Marwick, B. 2008. ``Measuring pre-processing in unretouched flaked stone artefact assemblages". Peer-reviewed presentation at the Australian Archaeological Association Annual Conference, Noosa Dec 3-6, Australia

\ind Marwick, B. 2008. ``Hoabinhian flaked stone artefact palaeoeconomics and palaeoecology". Peer-reviewed presentation at the Society of American Archaeology, Vancouver, March 2008, Canada

\ind Marwick, B. 2008 .``Ceramics of the three tributaries Luang Prabang, Lao PDR". Peer-reviewed presentation at the  Society of American Archaeology, Vancouver, March 2008, Canada

 \bigskip
 
 %% Talks at UW
 
 \marginhead{\sffamily {\vskip 0.3em} invited  \newline scholarly \newline talks \newline within UW}

\medskip

\ind Marwick, B. ``Computational methods for the analysis of unstructured text". UW Department of Linguistics’  Computational Linguistics Group, 4 Feb 2014. Invited presentation.

\ind Marwick, B. ``Pleistocene language evolution and raw material transfers". UW Linguistics Department. 22 Nov 2013. Invited colloquium

\ind Marwick, B. ``Mobile GIS for intensive archaeological survey of Holocene forager sites in arid South Australia". GIS Day Lightning Talk,  for the UW Geography Department 20 Nov 2013. Invited presentation.

\ind Marwick, B. and I Kretzler 2013. ``How to get students to read a lot. Distant reading in archaeological theory seminar". Ignite presentation for the UW Center for Teaching and Learning eText workshop 24 Oct 2013 Invited presentation.

\ind Marwick, B. 2012 ``Cultural Phylogenetics of Religion using Thai Bronze Buddha Statues". UW Centre for Statistics and Social Sciences, 4 April 2012. Invited presentation.


 
%% Service

\marginhead{\sffamily {\vskip 0.35em} service at UW}

\medskip

\noindent\emph{Anthropology Department \vspace{0.01in}}

\ind Departmental web site committee, 2010-current

\ind Departmental undergraduate curriculum coordination committee, 2013-current

\ind Departmental sub-faculty appointments committee, 2012-2013

\ind Departmental honours committee, 2012-2013

\ind Departmental honours coordinator, 2009-2010

\ind Departmental Self-Sustaining MA Degree Program in Public Anthropology planning committee, 2009-2010

\ind Archaeology Program undergraduate Archaeological Sciences Option coordinator, 2013-2014

\ind Archaeology Program teaching schedule coordinator, 2013-2014

\ind Archaeology Program graduate Comprehensive Exam coordinator, 2012-2014

\ind Archaeology Program Seminar coordinator, 2009-2013

 \vspace{0.05in}

\noindent\emph{Service elsewhere on campus\vspace{0.01in}}

\ind Adjunct Curator, Archaeology Department, Burke Museum, 2010--current

\ind Affiliate faculty, UW IGERT Program in Evolutionary Modeling, 2010--current

\ind Affiliate faculty, UW Quaternary Research Center, 2010--current

\ind Affiliate faculty, UW Center for Statistics and Social Sciences, 2009--current

\ind Affiliate faculty, UW Center for Southeast Asian Studies, 2009--current




ad-hoc peer-reviewer, UW Royalty Research Fund
2010, faculty adviser, South East Asia Center Graduate Student Conference
2009, South East Asia Center MA Program admissions 




\ind  Kieran Healy. 2006. \emph{\href{http://www.lastbestgifts.com}{Last Best Gifts: Altruism and the Market for Human Blood and Organs}}. Chicago:~University of Chicago Press. \vspace{0.05in}

\ind \hspace{0.35in} \footnotesize Winner, Association for Research on Nonprofit Organizations and Voluntary Action (ARNOVA) Outstanding Book Prize. Finalist, C. Wright Mills Award. 

\vspace{-0.075in}

\normalsize

\bigskip
\noindent\emph{Journal articles \vspace{0.05in}}
 
%% Use revnumerate environment if numbered publications are needed. 
%% (Include it above in the preamble).
%% \renewcommand{\labelenumi}{\textsc{a}\theenumi.}
%% \begin{revnumerate}

\ind Forthcoming. Kieran Healy and James Moody. ``Data Visualization in Sociology.'' \emph{Annual Review of Sociology.}

\ind Marion Fourcade and Kieran Healy. 2013. ``\href{http://kieranhealy.org/files/papers/classification-situations.pdf}{Classification Situations: Life-chances in the Neoliberal Era}.'' \emph{Accounting, Organizations, and Society} 38:~559--572.

\ind Kieran Healy and Kimberly R. Krawiec. 2012. ``\href{http://kieranhealy.org/files/papers/custom-contract-kidney.pdf}{Custom, Contract, and Kidney Exchange}.'' \emph{Duke Law Journal} 62:~645--670. 

\ind Kieran Healy. 2011. ``Counting and Commodifying.'' \emph{Washington University Journal of Law and Policy}. 35:~337--347.

\ind Marion Fourcade and Kieran Healy. 2007. ``\href{http://arjournals.annualreviews.org/doi/pdf/10.1146/annurev.soc.33.040406.131642}{Moral Views of Market Society}.'' \emph{Annual Review of Sociology} 33:~285--311. 

\ind Kieran Healy. 2006. ``\href{http://www.kieranhealy.org/files/papers/presumed-consent.pdf}{Do Presumed Consent Laws Raise Organ Procurement Rates?}'' \emph{DePaul Law Review} 55:~1017--1043. 

\ind Kieran Healy. 2004. ``\href{http://www.kieranhealy.org/files/papers/asr2004.pdf}{Altruism as an Organizational Problem: The Case of Organ Procurement}.''
 \emph{American Sociological Review} 69:~387--404.

\ind Kieran Healy. 2002. ``\href{http://www.kieranhealy.org/files/papers/jpp.pdf}{Digital Technology and Cultural Goods}.'' \emph{Journal of
  Political Philosophy} 10:~478--500. 

\ind Kieran Healy. 2002. ``\href{http://www.kieranhealy.org/files/papers/culture-newecon.pdf}{What's New for Culture in the New Economy?}'' \emph{Journal
  of Arts Management, Law and Society} 32:~86--103. 


\ind Kieran Healy. 2000. ``\href{http://www.kieranhealy.org/files/papers/embed-alt.pdf}{Embedded Altruism: Blood Collection Regimes and the European
  Union's Donor Population}.'' \emph{American Journal of Sociology} 105:~1633--1657.


\ind Kieran Healy. 1999.  ``\href{http://www.kieranhealy.org/files/papers/ts.pdf}{The Emergence of HIV in the U.S. Blood Supply: Organizations,
  Obligations and the Management of Uncertainty}.'' \emph{Theory and Society} 28:~529--558.


\ind Bruce Western and Kieran Healy. 1999. ``\href{http://www.kieranhealy.org/files/papers/western-healy99.pdf}{Explaining the OECD Wage Slowdown:
Recession or Labor Decline?}''  \emph{European Sociological Review}
15:~233--249.


\ind  Kieran Healy. 1998.  ``\href{http://www.kieranhealy.org/files/papers/constraint98.pdf}{Conceptualising Constraint: Mouzelis, Archer and the concept of
  social structure}.'' \emph{Sociology} 32:~509--522. 

%\end{revnumerate}
%\newpage
\bigskip

\noindent\emph{Book chapters \vspace{0.05in}}
% \renewcommand{\labelenumi}{\textsc{c}\theenumi.}
% \begin{revnumerate}

\ind Kieran Healy. Forthcoming. ``Social Structure, Gifts and Norms in \emph{The Story of Qiu Ju},'' in \emph{Norms and Values: The Role of Social Norms as Instruments of Value Realisation}, edited by Michael Baurmann, Geoffrey Brennan, Robert E. Goodin and Nicholas Southwood. Baden Baden: Nomos Verlag.

\ind Kieran Healy. 2008. ``Lo Scambio di Doni,'' in \emph{L'Altro in Me: Dono del Sangue fra Culture, Pratiche e Identità}, edited by Annamaria Fantauzzi. Milano: \textsc{avis} Nazionale, 36--42. 

\ind Kieran Healy. 2007. ``Sociology,'' in \emph{A Companion to Contemporary Political Philosophy} (Second Edition), edited by Robert E. Goodin, P. Pettit and Thomas Pogge. New York: Blackwell, 90--122. 

\ind  Kieran Healy. 2004. ``Sacred Markets and Secular Ritual in the Organ Transplant
Industry,'' in \emph{The Sociology of the Economy}, edited by Frank Dobbin. New
York: Russell Sage, 336--359.

\ind Bruce Western and Kieran Healy.  2001.  ``Wage Growth and Labor Decline in the
Industrialized Democracies, 1965--1993,'' in \emph{Unemployment in the New
  Europe}, edited by Nancy Bermeo. New York: Cambridge University Press,
121--144.

 \ind  Kieran Healy. 1998. ``The New Institutionalism and Irish Social Policy,'' in
\emph{Social Policy in Ireland: Principles, Practice and Problems}, edited by
Se\'{a}n Healy and Brigid Reynolds. Dublin: Oak Tree Press, 59--83.


%\end{revnumerate}

\bigskip 

%\newpage
\noindent\emph{Essays and reviews \vspace{0.05in}}

%\renewcommand{\labelenumi}{\textsc{r}\theenumi.}
%\begin{revnumerate}

\ind Kieran Healy. 2011. ``\href{http://www.kieranhealy.org/files/reviews/karpik-review.pdf}{Judgment and Distinction}.'' \emph{Socio--Economic Review} 9:~787--800. 

\ind Kieran Healy. 2011. ``\href{http://polmeth.wustl.edu/methodologist/tpm_v18_n2.pdf}{Choosing your Workflow Applications}.'' \emph{The Political Methodologist} 18 (2):~9--18. 

\ind Kieran Healy. 2009. \href{http://www.journals.uchicago.edu/doi/pdf/10.1086/605757}{Review} of \emph{Pop Finance} by Brooke Harrington. \emph{American Journal of Sociology} 115:~309--12.

\ind Kieran Healy. 2007. ``\href{http://www.kieranhealy.org/files/reviews/socforum-article.pdf}{A Wealth of Notions}.'' Review
Essay on \emph{Freakonomics} by Steven Levitt and Stephen Dubner. \emph{Sociological Forum} 22:~119--125. 

\ind  Kieran Healy. 2006. ``Sacred.'' In \emph{International Encyclopedia of Economic Sociology}, edited by Jens Beckert and Milan Zafirovski. London: Routledge, 588--589. 

\ind  Kieran Healy. 2005. \href{http://www.kieranhealy.org/files/reviews/klinenberg.pdf}{Review} of \emph{Heat Wave} by Eric Klinenberg. \emph{Imprints} 8:~283--289.

\ind  Kieran Healy. 2005. \href{http://www.kieranhealy.org/files/reviews/fox.pdf}{Review} of \emph{An R and S-PLUS Companion to Applied Regression}, by John Fox. \emph{Sociological Methods and Research} 34:~137--140.

\ind  Kieran Healy. 2005. ``\href{http://www.kieranhealy.org/files/reviews/henwood.pdf}{After the Ball was Over}.'' Review of \emph{After the New
  Economy} by Doug Henwood. \emph{European Economic Sociology Newsletter} 6 (3):~37--38.

\ind  Kieran Healy. 2004. ``The Abundance of the Heart.'' Review of \emph{A Man After His Own Heart} by Charles
Siebert. \emph{Australian Review of Public Affairs}, October. Reprinted in the
\emph{Australian Financial Review}, October 22nd.

\ind  Kieran Healy. 2003. \href{http://links.jstor.org/sici?sici=0094-3061%28200303%2932%3A2%3C252%3AAEATOC%3E2.0.CO%3B2-F}{Review} of \emph{Against Essentialism} by Stephan Fuchs.
\emph{Contemporary Sociology} 32:~252--254.

\ind  Kieran Healy. 2001. Review of \emph{Market Society} by Don Slater and Fran Tonkiss. \emph{European Economic Sociology Newsletter} 3 (1):~31--32.


\ind  Kieran Healy. 1999. \href{http://links.jstor.org/sici?sici=0094-3061%28199903%2928%3A2%3C210%3ACPRCAS%3E2.0.CO%3B2-C}{Review} of \emph{Comparative Politics} by Mark Irving Lichbach and Alan S.
Zuckerman. \emph{Contemporary Sociology} 28:~210--211.


\ind  Kieran Healy. 1998. \href{http://www.kieranhealy.org/files/reviews/rule.pdf}{Review} of \emph{Theory and Progress in Social Science} by James Rule.  \emph{Theory
  and Society}, 27:~435--441.

 
% %\end{revnumerate}
 \bigskip

%% Presentations
\marginhead{\sffamily {\vskip 0.5em}selected \newline invited talks \newline since 2007}
\medskip


\ind ``Classification Situations.'' Yale University Center for Cultural Sociology, 2013.
 
\ind ``Scores and Classes.'' University of Pennsylvania, 2012.

\ind ``The Performativity of Networks.'' Max Planck/Sciences Po Center, Paris, 2012. 
 
\ind ``Specialization and Status in Philosophy.'' Princeton University, 2010. 

\ind Invited Discussant, ``For Love or Money?'', Center for the Interdisciplinary Study of Work and Social Capital, Washington University in St.\,Louis School of Law, 2010. 

\ind ``Gift Fetishism and the Market for Human Organs.'' CAL Visiting Scholar Lecture Series, James Madison University, 2009. 

\ind ``Specialization and Status in Philosophy.'' University of Chicago, Booth School of Business, 2009. 

\ind ``Specialization and Status in Philosophy.'' University of California, Berkeley, 2009. 

\ind ``Specialization and Status in Philosophy.'' University of Michigan, ICOS, 2009. 

\ind ``Specialization and Status in Philosophy.'' Columbia University 2009. 

\ind ``The Performativity of Networks.'' Yale University, 2009. 

\ind ``The Performativity of Networks.'' Stanford University Graduate School of Business, 2008. 

\ind ``The Performativity of Networks.'' Harvard/MIT Joint Seminar in Economic Sociology, 2008. 

\ind ``Last Best Gifts: Altruism and the Market for Human Blood and Organs.'' Center for History, Society and Culture, University of California at Davis, 2007. 

\ind ``Gift Fetishism and the Market for Human Organs.'' Department of Anthropology, University of Arizona, 2007. 

%\end{revnumerate}

\bigskip

%\newpage

\marginhead{\sffamily {\vskip 0.5em}selected \newline conference \newline presentations \newline since 2007}
\medskip

\ind ``Dealing with Awkward Relations.'' Conference on New Theoretical Directions in Economic Sociology, Stockholm, September 2013. 

\ind ``Credit Scores and the Moralization of Inequality.'' Annual Meetings of the American Sociological Association, New York, August 2013.
 
\ind ``Channeling Solidarity: Social Organization and Blood Donation in Response to 9/11.'' Annual Meetings of the American Sociological Association, New York, August 2013.

\ind Invited discussant, ``Religion and Generosity.'' American Sociological Association/American Society for Religion, joint session, Denver, August 2012.

\ind Invited discussant, ``Philanthrophy and Real Utopia.'' Meetings of the American Sociological Association, Denver, August 2012. 

\ind ``Ranking and the Gourmet Report.'' Meetings of the Central Division of the American Philosophical Association, Chicago, 2012. 

\ind ``Dealing with Difficult Relations.'' Annual Meetings of the American Sociological Association, Las Vegas, 2011.

\ind ``Economic Categories in Neoliberal Society.'' Annual Meetings of the Society for the Advancement of Socio-Economics, Madrid, 2011.

\ind ``Economic Categories in Neoliberal Society.'' Annual Meetings of the Social Science History Association. Chicago, 2011. 

\ind Invited discussant, ``Markets for Health or Healthy Markets?'' Annual Meetings of the American Sociological Association, Atlanta, 2010. 

\ind ``Economic Categories and Claims.'' Conference on The Politics of Markets: Controversies, tools and policies, Berkeley, 2009.

\ind Invited speaker, ASA Culture Section 20th Anniversary Symposium, ``Culture and Economy,'' Boston, 2008.

\ind Invited discussant, conference on Norms and Values, ZiF center, University of Bielefeld, Germany, 2008. 

\ind ``Economic Categories and the Claims of Neoliberal Society.'' Invited Session on Culture and Markets. Annual Meetings of the American Sociological Association, New York, 2007.

\ind ``The Performativity of Networks.'' Special Session on Money in Movement: Markets, Circuits and Networks. Annual Meetings of the American Sociological Association, New York, 2007.

\ind Presider, Regular Session on the Sociology of Knowledge. Annual Meetings of the American Sociological Association, New York, 2007. 

\ind Discussant, Book Panel on Steven Levitt and Stephen Dubner's \emph{Freakonomics}. Annual Meetings of the Eastern Sociological Society, Philadelphia, 2007. 

\bigskip 

\marginhead{\sffamily {\vskip 0.6em}grants,\newline honors, \newline \& awards}
\medskip

\ind Residential Fellowship, Center for Advanced Study in the Behavioral Sciences, Stanford University, 2008-09.

\ind Association for Research on Nonprofit Organizations and Voluntary Action (ARNOVA) Outstanding Book Prize, 2007.

\ind Finalist, Society for the Study of Social Problems (SSSP), C. Wright Mills Award, 2007.

\ind Rogers Program in Law and Society, Faculty Research Award, University of Arizona, 2006.

\ind Participant, Summer Institute on \emph{Economy and Society: Trajectories of Capitalism}, Center for Advanced Study in the Behavioral Sciences, 2006.

\ind University of Arizona SBSRI/Center for Applied Spatial
Analysis. Geographical Information Systems Research Assistance
Program Award. ``The Geography of Organ Procurement'', 2003.

\ind American Sociological Association, Dissertation Award, 2002.

\ind University of Arizona Prop.\,301 Information Technology/Information Science Fund Award, 2002.

\ind National Science Foundation Doctoral Dissertation Research Improvement Award, 2000.

\ind Graduate Fellow, Fellowship of Woodrow Wilson Scholars, Princeton University,  1998--2000. 

\ind Noah Cotsen Junior Teaching Fellowship, Princeton University, 1998--1999.

\ind General Examinations with Distinction, Princeton University, 1998.

\ind Graduate Fellowship, Princeton University, 1995--1998.

\ind College Scholar, University College, Cork, 1993--1994.

\ind College Undergraduate Scholarship, University
College, Cork, 1991--1993.

\bigskip 


\marginhead{\sffamily {\vskip 1.12em}service to the \newline profession}
\medskip

\medskip


\marginhead{{\vskip 0.9em}Service to the \newline Profession}
\medskip

\medskip

\end{document}
