%% Talks and presentations - special invited talks

\marginhead{\sffamily {\vskip 0.3em} talks \& \newline presentations}

\medskip

\noindent\emph{Invited scholarly talks and workshops (since 2009)\vspace{0.01in}}

\medskip

\ind Shafizadeh, S. and B. Marwick 2021. ``Levallois Technology in Iran: Analysis of assemblages from Cheshmeh-Agha, Farsan and Mirak". Poster at the International Symposium of Knappable Materials, remote, Tarragona, Spain, 4-7th October 2021,  \url{https://wwwa.fundacio.urv.cat/congressos/13iskm2021/home}  Data \& R code:  \url{https://github.com/benmarwick/ISKM2021-Setareh-Marwick-Iran}  

\ind Thompson, Tj., B. Marwick, N. Mitchell, R. Fullagar, L. Wallis, M. Smith, \& C. Clarkson 2021. ``Artefact orientations and site formation processes at Madjedbebe, northern Australia". Presentation at the International Symposium of Knappable Materials, remote, Tarragona, Spain, 4-7th October 2021,  \url{https://wwwa.fundacio.urv.cat/congressos/13iskm2021/home}  Data \& R code online at  \url{https://github.com/benmarwick/mjblithicorientations}  

\ind Craig, J., B. Marwick, D. Bulbeck, Suryatman, S. O’Connor. 2021. ``Stabilizing Selection in Informal Stone Artifact Technologies and Procurement Strategies at Talimbue, Sulawesi, Indonesia". Presentation at the International Symposium of Knappable Materials, Tarragona, Spain, 4-7th October 2021, remote,  \url{https://wwwa.fundacio.urv.cat/congressos/13iskm2021/home}  Data \& R code online at   \url{https://github.com/benmarwick/talimbuelithics}     

\ind Habedank, Q., I. A. Osuna, T. S. Pham, B. Marwick 2021. ``Late Pleistocene flaked artefact morphometry and technology at Mau A, northern Vietnam". Presentation at the International Symposium of Knappable Materials, remote, Tarragona, Spain, 4-7th October 2021,  \url{https://wwwa.fundacio.urv.cat/congressos/13iskm2021/home} Data \& code:  \url{https://github.com/benmarwick/maualithics} 

\ind Marwick, B. 2021. ``Mechanisms in archaeological explanation: Is a palaeo-sociology possible?  Presentation at the Workshop Mecabiosoc. Mechanisms in Biology and the Social Sciences. Uned. Senda del Rey. 28040 Madrid, 27th-28th September, remote, slides  

\ind Marwick, B. 2021. ``Digital Ecosystems in Archaeological Science: A History and Taxonomy of R packages in Archaeology. Presentation at the Computer Applications and Quantitative Methods in Archaeology Conference. 14-18 June 2021, remote,  \url{https://github.com/benmarwick/CAA2021}  

\ind Wang, L. and B. Marwick 2021. ``A Bayesian network modeling approach to examine social changes using burial data. Presentation at the Computer Applications and Quantitative Methods in Archaeology Conference. 14-18 June 2021, remote 

\ind Marwick, B., D. Matzig, F. Reide 2021. ``Bayesian inference of material culture phylogenies using continuous traits from the archaeological record.  Presentation at the Cultural Evolution Society Conference, Sapporo, remote, Japan, 9-11 June 2021  \url{https://github.com/benmarwick/CES2021}, Presentation at the International Symposium of Knappable Materials, remote, Tarragona, Spain, 4-7th October 2021  \url{https://wwwa.fundacio.urv.cat/congressos/13iskm2021/home}  

\ind Marwick, B. 2021. ``Doing modern archaeological science: what are the options for openness? Invited presentation for IsoArcH: Open Science in Archaeology, A United Kingdom Reproducibility Network Workshop, 20 May 2021,  \url{https://osf.io/w2gqe/}  

\ind Marwick, B. 2022. ``Like the layers of an onion: Reproducibility and Transparency for quantitative research. University of Wollongong Data and Decision Science Network meeting, 29 April 2022, remote, slides:  \url{https://osf.io/5n6k9}  

\ind Panelist on PEMSEA Panel 6: The Future Southeast Asian Archaeology in the U.S. (13 Sept 2021) This panel discussion was part of a series hosted by the Program on Early Modern Southeast Asia.  \url{https://www.facebook.com/watch/live/?ref=watch_permalink&v=396716412049347}   

\ind Marwick, B. 2021. ``Improving the transparency and reproducibility of historical archaeological research: A case study in teaching how slavery ended at New River Village, Nevis. Presentation Digital Archaeological Archive of Comparative Slavery Conversations Series. 25 June 2021, remote,  \url{https://www.daacs.org/research/discover-with-daacs/}  

\ind Marwick, B. 2021. ``Let's Connect. Celebrating the 100th episode of the Down Ancient Trails Series: \& Celebrating the discovery of the first Palaeolithic artefact in India on 30th May, 1863. Invited presentation for the Sharma Center for Heritage, Chennai, India. 31 May, remote 

\ind Marwick, B. and Pham Thahn Son 2021 ``An Update on the Sonvian-Hoabinhian Controversy: Shape Analysis of Flakes and Cores from Mau A, Northern Vietnam" Paper presented at the Society of American Archaeology Annual Meeting, April 2021. 

\ind Chen, Y and B. Marwick 2021 ``Correlations between Gender and Research Topics at Three Major Archaeology Conferences." Paper presented at the Society of American Archaeology Annual Meeting, April 2021. 

\ind Wang, L. and B. Marwick 2021 ``Bayesian Exponential Random Graph Modeling of an Iron Age Burial Network in Northeastern Taiwan." Paper presented at the Society of American Archaeology Annual Meeting, April 2021.  

\ind Park, G. and B. Marwick 2021 ``Understanding the transition of technology and subsistence strategies, based on cultural evolution during the Late Pleistocene in Korea." Paper presented at the Cross Disciplinary Approaches to Prehistoric Demography – CROSSDEM21,  \url{https://events.au.dk/crossdem2021}  

\ind Wang, L. and B. Marwick 2020 "The practice of open science in archaeology using R and online digital repositories in a case study research." Poster presented at the Computer Applications and Quantitative Methods in Archaeology, 2020,  \url{https://sites.caa-international.org/au/2020-conference-poster-session/}   

\ind ``Dialogues with the Past - Nordic Graduate School in Archaeology: Reproducible Quantitative Research in Archaeology: Doing Open Science Archaeology (using R)" I was the lead instructor for a four-day remote workshop with 10 students at Scandinavian universities  \url{https://www.hf.uio.no/iakh/english/research/dialogues-with-the-past/courses/reproducible-quantitative-research-in-archaeology-.html} \&  \url{https://osf.io/hrqnu/}  

\ind ``Galisonian Logic Devices as Affordances for Decolonizing Archaeology" Remote presentation in the Garrod Research seminar series of the McDonald Institute for Archaeological Research, University of Cambridge. 18 Feb 2021,  \url{https://www.youtube.com/watch?v=iqJzhOZ7Auo}  

\ind ``Open Access, Open Data, and Open Methods: Three steps to transparency that are redefining archaeological science" Remote keynote for ARCHON Day at the ARCHON Research School for Archaeology, Amsterdam, the Netherlands. 30 October 2020.  \url{http://doi.org/10.17605/OSF.IO/9XNMG} 

\ind ``Tool-Driven Revolutions in Archaeological Science: Open Source and Open Science as Transcendental Tools" Remote Seminar for The Archaeological Information Interest Group at the Archaeology Centre at the University of Toronto, 24 September 2020 3pm  \url{https://www.youtube.com/watch?v=VKVlcMCLm04} 

\ind Marwick, B. \href{https://github.com/benmarwick/VNU-Geoscience-mapping-with-R-Workshop}{``Reproducible geoscience research: Stratigraphic data visualization using R"} for the Vietnam National University Geology Department, Hanoi 17 May, 2020 [online]

\ind Marwick, B. \href{http://www.sharmaheritage.com/down-ancient-trails-archaeology-forum-}{``How did modern humans make their way into mainland Southeast Asia? New data on the Paleolithic from excavations in China, Myanmar, Vietnam, and Australia"}, Down Ancient Trails Seminar Series, Sharma Centre for Heritage Education, India, 12 May 2020  [online]

\ind Marwick, B. \href{https://github.com/benmarwick/VNU-Geoscience-mapping-with-R-Workshop}{``Reproducible geoscience research: Mapping using R"} for the Vietnam National University Geology Department, Hanoi 10 May, 2020  [online]

\ind Marwick, B. ``The landscape of open data, data sharing, and data reuse in archaeology", hosted by the Arctic section of the NSF Office of Polar Programs, 21-22 April 2020 [online]

\ind Marwick, B. ``How did modern humans make their way into mainland Southeast Asia? New data on the Paleolithic from excavations in China, Myanmar, Vietnam, and Australia", for the Department of Archaeology, Sichuan University, China, 27 Mar 2020 [online]

\ind Marwick, B. \href{https://benmarwick.github.io/2019-12-09-brown/}{``Reproducible Research in Archaeology and Anthropology"}, for the Brown University Anthropology Department 9 Dec, 2019 [online]

\ind Marwick, B. ``Making sense of the Sonvian: Cultural taxonomies in the Palaeolithic of mainland Southeast Asia" for the workshop ‘All these fantastic cultures? Cultural taxonomies in the Palaeolithic - old questions, novel perspectives’, Aarhus University, Sandbjerg Estate, Denmark, 25-30 Nov, 2019 

\ind Marwick, B. ``Experiences of Archaeological field research in Myanmar, Vietnam and Australia" for the Department of Anthropology, National Taiwan University, Taipei, Taiwan, 27 Sept 2019

\ind Marwick, B.  ``How did modern humans make their way into mainland Southeast Asia? New data on the Paleolithic from excavations in China, Myanmar, Vietnam, and Australia", for the workshop ``New Practices in Late Palaeolithic Archaeology and Lithic Analysis" for the Department of Anthropology, National Cheng Kung University, Tainan, Taiwan, 25 Sept 2019 

\ind Marwick, B. ``Lithic data analysis using R" for the Department of Anthropology, National Cheng Kung University, Tainan, Taiwan, 24 Sept 2019 

\ind Marwick, B. \href{https://osf.io/e3x7u/}{``Using R and related tools for reproducible research in Archaeology"} for the Department of Anthropology, National Cheng Kung University, Tainan, Taiwan, 23 Sept 2019 

\ind Marwick, B. \href{https://osf.io/ktrns/}{``Pseudoarchaeology as stigmatised knowledge: Why is this dangerous to society?"} for the Department of Anthropology, National Taiwan University, Taipei, Taiwan, 19 Sept 2019 

\ind Marwick, B. ``Using R to write reports and journal articles" for the Department of Anthropology, National Taiwan University, Taipei, Taiwan, 18 Sept 2019

\ind Marwick, B. ``How did modern humans make their way into mainland Southeast Asia? New data on the Paleolithic from excavations in China, Myanmar, Vietnam, and Australia", for the workshop ``New Practices in Late Palaeolithic Archaeology and Lithic Analysis", Department of Anthropology, National Taiwan University, Taipei, Taiwan, 17 Sept 2019

\ind Marwick, B. ``Using R and Related Tools for Reproducible Research in Stone Artefact Archaeology", for the workshop ``New Practices in Late Palaeolithic Archaeology and Lithic Analysis", Department of Anthropology, National Taiwan University, Taipei, Taiwan, 17 Sept 2019

\ind Marwick, B. \href{https://benmarwick.github.io/2019-09-14-morph2019/}{``Transparent and Reproducible Archaeological Research Using Open Data Science Tools"} for the MORPH2019 Conference, Sendai, Japan, 14 Sept 2019 

\ind Marwick, B.  ``Moving on from Movius: Recent research in Pleistocene archaeology in Myanmar", Palaeolithic \& Quaternary seminar series National Museum of Ethnology, Osaka, Japan, 12 Sept 2019

\ind Marwick, B. \href{https://benmarwick.github.io/2019-09-10-nara/}{``Transparent and Reproducible Archaeological Research Using Open Data Science Tools"} for the National Research Institute for Cultural Properties, Nara, Japan, 11 Sept 2019 

\ind Marwick, B. \href{https://osf.io/dwks9/}{``Git for Archaeological Science"} for the National Research Institute for Cultural Properties, Nara, Japan, 10 Sept 2019 

\ind Marwick, B. \href{https://osf.io/ubvcp/}{``Modern tools and approaches to scientific data management, analysis, visualization, collaboration in archaeology and cultural heritage"} for the National Research Institute for Cultural Properties, Nara, Japan, 10 Sept 2019  

\ind Marwick, B.  \href{https://osf.io/4a6cw/}{``Open Access, Open Data, and Open Methods: Three steps to transparency that are redefining archaeological science"} for the National Research Institute for Cultural Properties, Nara, Japan, 10 Sept 2019 

\ind Marwick, B.  ``Reproducibility and Transparency in Archaeology: Ongoing work and activities". Invited workshop presentation at the Project TIER Fellows Conference. Haverford College, Philadelphia, 4 June 2019

\ind Marwick, B. \href{https://github.com/benmarwick/Marwick-CSSS-May-2019-Reproducibility }{Writing reproducible research with R and Markdown}. Invited workshop presentation at the UW Center for Statistics and the Social Sciences (CSSS) 20th Anniversiary Conference. UW-Seattle, 23 May 2019, WA. 

\ind Marwick, B. \href{https://github.com/benmarwick/Stirling-May-2019-digital-heritage-big-data }{``Community Data Science meets Digital Heritage: Controversies about World Heritage Sites in the Online Community of Wikipedia"}, keynote presentation for the conference 'Digital Heritage in a World of Big Data', University of Stirling, Scotland, 14 May, 2019 

\ind Marwick, B. ``Big Data and Tool-driven Revolutions in Archaeological Science" for the Archaeology Department of Environment Heritage Scotland, Edinburgh 13 May, 2019 

\ind Marwick, B.  ``Writing reproducible research with R and Markdown". Invited workshop presentation at the Northwest Data Science Summit. UW-Seattle, 8 May 2019, WA.

\ind Marwick, B. \href{https://github.com/benmarwick/March-2019-Cambridge-Big-Data-Archaeology }{``Big Data and Tool-driven Revolutions in Archaeological Science"} for the conference 'Big Data in Archaeology: Practicalities and Possibilities' at University of Cambridge, 27-28 March, 2019 

\ind Marwick, B. \href{https://github.com/benmarwick/Marwick-UCL-March-2019-Reproducibility }{``Making archaeological science transparent, open and reproducible with R and friends: A short workshop"} Institute of Archaeology, University College London, 6 March, 2019 

\ind Marwick, B. ``How did modern humans make their way into mainland Southeast Asia? New data on the Paleolithic from excavations in China, Myanmar, Vietnam, and Australia", Institute of Archaeology, University College London, 7 March, 2019

\ind Marwick, B. ``Emerging norms in open data and open methods", Paris Dialogue on Archaeological Lidar, l'École française d'Extrême-Orient (Paris), 11 Dec, 2018

\ind Marwick, B. ``Moving on from Movius: Recent research in Pleistocene archaeology in Myanmar", Palaeolithic \& Quaternary seminar series, Oxford University, 29 Nov 2018

\ind Marwick, B. ``Four ordered principles to improve the reproducibility of research", All Souls College, Oxford University, 28 Nov 2018

\ind Marwick, B. ``Making archaeological science transparent, open and reproducible with R and friends: A short workshop",  School of Archaeology, Oxford University, 28 Nov 2018

\ind Marwick, B. ``How did modern humans make their way into mainland Southeast Asia? New data on the Paleolithic from excavations in China, Myanmar, Vietnam, and Australia", Invited presentation, University of Oxford, Institute of Archaeology, Palaeolithic \& Quaternary seminar, 29 Nov 2018

\ind Marwick, B. ``Four ordered principles to improve the reproducibility of research"=, Invited presentation, University of Oxford, All Souls College, 28 Nov 2018

\ind Marwick, B. ``How did modern humans make their way into mainland Southeast Asia? New data on the Paleolithic from excavations in China, Myanmar, Vietnam, and Australia", Invited presentation, University of Oregon, Department of Anthropology and the Center for Asia and Pacific Studies, 23 Oct 2018

\ind Marwick, B. ``Open Access, Open Data, and Open Methods: Three steps to transparency that are redefining archaeological science", Invited presentation, University of Oregon, Department of Anthropology, 22 Oct 2018

\ind Marwick, B. \href{https://osf.io/ybj43/}{Southeast \& East Asian Social Sciences Workshops for Transparency and Reproducibility.} A series of invited talks and workshops at Silpakorn University, Bangkok, Vietnam National University, Hanoi, National Taiwan University, Taipei, and Seoul National University, Seoul. September 8-20, 2018

\ind Marwick, B. ``Archaeological Science, Archaeology of Science, and Tools for Closing the Gap between Practice and Ideals" Invited presentation, US-Serbia \& West Balkan Data Science Workshop, Belgrade, Serbia, August 26-28 2018.

\ind Marwick, B. Convener and Chair, \href{https://jsis.washington.edu/seac/news/roundtable-discussion-myanmar-rohingya-crisis-2/}{Roundtable Discussion on Myanmar and the Rohingya Crisis} UW Southeast Asia Centre, 11 Jan 2018, Seattle, with 5 UW faculty panelists

\ind Marwick, B. 2018. ``Adaptations to sea level change and transitions to agriculture at Khao Toh Chong rockshelter, Peninsular Thailand", Invited presentation, Washington State University, 18 Jan 2018

\ind Marwick, B. 2017 ``Madjedbebe, Australia's earliest archaeological site Site formation, artefact movement and human behaviour", Invited workshop presentation at the ‘Using Archaeological Sciences to Address Human Behaviour’ workshop, University of Tübingen, Germany, 12-17 Nov, 2017

\ind Marwick, B. 2017. ``rrtools: writing reproducible research", Invited workshop presentation presented at the DataONE WholeTale ‘Prov-a-thon’, University of Illinois, August 31–September 1, 2017

\ind Marwick, B. 2017. \href{https://github.com/benmarwick/berlinsummerschoolkeynote}{``Extracting Sunbeams Out of Cucumbers: Why Archaeology Isn't a Science, and How It Can Become One"} Keynote presentation, Summer School on Computational Archaeology, Freie Universität Berlin, 17-21 July 2017

\ind Marwick, B. 2017. ``A Practising Academic’s View of Field Data Collection Technologies." Workshop on Archaeological Database Evaluation, Cotsen Institute of Archaeology, UCLA,  Jun, 9, 2017. Invited Presentation.

\ind Marwick, B. 2017. \href{https://github.com/benmarwick/ETH-Zurich-ZuKoSt-Reproducible-Research-Compendia-via-R-packages}{``Reproducible Research Compendia via R packages."} ZüKoSt: Seminar on Applied Statistics, ETH-Zurich,  Mar, 2, 2017. Invited Presentation.

\ind Marwick, B. 2017. `Using R in the development sector in Myanmar and Vietnam: Benefits, challenges, and impacts of open source tools for working with data." Mathematical and Data Sciences for Development Forum, ETH-Zurich,  Mar, 1, 2017. Invited Presentation.

\ind Marwick, B. 2017. \href{https://www.youtube.com/watch?v=k3Wv4Cnr0Nc}{``The Galisonian program, hard cores, and mirror recursion in Archaeological science."} Conference on Critical Perspectives on the Practice of Digital Archaeology, Harvard University,  Feb, 3, 2017. Keynote Presentation.

\ind Marwick, B. 2016. ``Geoarchaeology of tektites in mainland Southeast Asia." Symposium on Anh Khe Archaeology, Institute of Archaeology, Vietnam, Oct, 30, 2016. Invited Presentation.

\ind Marwick, B. 2016. \href{https://github.com/benmarwick/UOW-NIASRA-2016-talk}{``Computational reproducibility in research and teaching: A case study from archaeology."} University of Wollongong National Institute for Applied Statistics Research Australia, May, 25, 2016. Invited Presentation.

\ind Marwick, B. 2016. ``Moving on from Movius: Recent research in Pleistocene archaeology in Myanmar." Monash University Archaeology Department, Melbourne, May, 17, 2016. Invited Presentation.

\ind Marwick, B. 2016. \href{https://github.com/benmarwick/Monash-Wombat-2016-talk}{``Computational Reproducibility in Archaeological Research: Basic Principles and a Case Study of Their Implementation."} Monash University Econometrics and Business Statistics, Melbourne, May, 17, 2016. Invited Presentation.

\ind Marwick, B. 2016. ``Mau A and the Hoabinhian-Sonvian transition." Vietnam Institute of Archaeology, Hanoi, Vietnam, 6 May 2016. Invited Presentation.

\ind Marwick, B. 2015. ``Three styles of Darwinian evolution in the analysis of stone artefacts Which one to use in East/Southeast Asia?" Department of History, Kyung Hee University, Seoul, Korea, Mar 3, 2015. Invited Presentation.

\ind Marwick, B. 2014. ``Palaeolithic archaeology in mainland Southeast Asia". Department of Archaeology, University of Yangon, Myanmar. Jan 19, 2014. Invited Presentation.

\ind Marwick, B. 2014. ``A primer on reproducible research: Basic principles and common tools". Department of Applied Mathematics and Theoretical Physics, University of Cambridge. Nov 11, 2014. Invited Presentation.

\ind Marwick, B. 2013. ``Research Report on Middle Holocene Research in mainland Southeast Asia". Southeast Asia Archaeology Workshop, University of Hawaii-Manoa, April 2013. Invited Presentation.

\ind Marwick, B. 2013 ``The Hoabinhian of Southeast Asia and its relationship to global Pleistocene lithic technologies". International Symposium on the Palaeolithic Cultures in Taiwan and Its Surrounding Areas, Academia Sinica, Taitung, Taiwan, 29-31 March 2013.  Invited Presentation.

\ind Marwick, B. 2013 ``Pleistocene lithic technologies in Mainland Southeast Asia: How does the Hoabinhian fit in?"  International Conference on Recent Advances in the Archaeology of East and Southeast Asia. University of Wisconsin-Madison, Wisconsin, USA, March 15-16, 2013. Invited Presentation.

\ind Marwick, B. 2012 ``Cultural Phylogenetics of Religion using Thai and Lao Bronze Buddha Statues". Department of Archaeology, University College Dublin, Ireland. Nov 22, 2012. Invited Presentation.

\ind Marwick, B. 2009 ``Pleistocene Exchange Networks as Evidence of Language Evolution".  UBC/SFU Human Evolution, Culture and Cognition seminar series, UBC, Vancouver, Canada. Invited presentation

\bigskip

%% Talks and presentations - regular contributed papers

% \marginhead{\sffamily {\vskip 0.3em} contributed \newline scholarly \newline talks \& \newline presentations \newline (since 2008)}

\noindent\emph{Contributed scholarly talks \& presentations (since 2009)\vspace{0.01in}}

\medskip

\ind Marwick, B. and L. Wang \href{https://www.washington.edu/teaching/2020/04/02/34-teaching-integrity-in-empirical-archaeology-with-replication-assignments/}{Teaching Integrity in Empirical Archaeology With Replication Assignments}. Poster presented at the UW Centre for Teaching and Learning Symposium, 2 April 2020   

\ind Wang, L. and B. Marwick. Investigating social change during cultural contact period using geometric morphometry of artifact shapes from Iron Age Northeast Taiwan. Paper presented at the MORPH2019 meeting, 14-15 Sept, 2019, Sendai, Japan.

\ind Marwick, B. Four tools for writing reproducible research. Lightening presentation at the Northwest Data Science Summit. UW-Seattle, 8 May 2019, WA. 

\ind Schnee, I and B. Marwick \href{https://www.washington.edu/teaching/files/2019/04/Schnee.Ian_.pdf}{Active Enough? Assessing the Impact of Screens in Active-Learning Classrooms}. Poster presented at the UW Centre for Teaching and Learning Symposium, 17 April 2019 Winner Best Research Poster Prize. 

\ind Marwick, B. Invited discussant in the session "Paradigms Shift: New Interpretations in Mainland Southeast Asian Archaeology", Society of American Archaeology meeting, 10-14 April, 2019, Albuquerque, NM.

\ind Marwick, B.  and L. Wang \href{https://github.com/benmarwick/signatselect}{Identifying Signatures of Selection in Archaeological Sequences}. Presentation delivered at the Society of American Archaeology meeting, 10-14 April, 2019, Albuquerque, NM.  (I was also co-chair of this session "Practical Approaches to Identifying Evolutionary Processes in the Archaeological Record" with Enrico Crema)

\ind Park, G. and B. Marwick. \href{https://doi.org/10.17605/OSF.IO/YAGD2}{Change in Mobility and Site Occupation during the Late Pleistocene in Korea}. Poster presented at the Society of American Archaeology meeting, 10-14 April, 2019, Albuquerque, NM. 

\ind Wang, L. and B. Marwick. \href{https://doi.org/10.17605/OSF.IO/J59DF}{Investigating craft specialization and pottery standardization using geometric morphometry of vessel shapes from Iron Age Northeast Taiwan}. Poster presented at the Society of American Archaeology meeting, 10-14 April, 2019, Albuquerque, NM. 

\ind Marwick, B. Over-Research in International Archaeology. Presentation delivered at the Indo-Pacific Prehistory Association Congress, 23-28 September 2018, Hue, Vietnam

\ind Marwick, B. Nguyen Thi Mai Huong, Nguyen Tho Dinh, Pham Thanh Son, Nguyen Anh
Tuan, Maria Schaarschmidt, Conor Mcadams, and Richard Roberts. New Excavations at Nguom Rockshelter, Northern Vietnam: Insights into PreHoabinhian Technology in Mainland Southeast Asia. Presentation delivered at the Indo-Pacific Prehistory Association Congress, 23-28 September 2018, Hue, Vietnam

\ind Marwick, B. et al. {\href{https://osf.io/tz6s5/}{Modeling the Innovation and Extinction of Archaeological Ideas}}, presentation at the Society of American Archaeology meeting, 13-15 April, 2018, Washington DC.

\ind Marwick, B. and S. Schmidt 2018.  {\href{https://github.com/benmarwick/caa2018-Tubingen}{``Reproducible research in archaeology using R \& rrtools"}}, presentation at the Computer Applications and Quantitative Methods in Archaeology (CAA) Annual Conference, 2018, Tubingen, Germany, 19-21 Mar 2018.

\ind  Marwick, B. et al. 2017 ``Stratigraphy, site formation, and artefact taphonomy at Madjedbebe, NT" presentation at the Australian Archaeological Association Conference, 2017, Melbourne, Australia, 6-8 Dec 2017.

\ind  Yue H., B. Marwick, W. Huang, J. Zhang and B. Li  2017. ``Middle Pleistocene Lithic Technology at Guanyingdong, Guizhou Province, China".  Peer-reviewed presentation at the Society of American Archaeology conference, Apr 2017, Vancouver.

\ind  Marwick, B. 2017. ``Moving on from Movius: Recent research in Pleistocene archaeology in Myanmar".  Peer-reviewed presentation at the Society of American Archaeology conference, Apr 2017, Vancouver.

\ind Conrad, C., C. Higham, M. Eda and B. Marwick 2016 ``Hunter-Gatherer Foraging Adaptations at Spirit Cave and Banyan Valley Cave (Mae Hong Son Province, Northwest Thailand) During the Late Pleistocene and Holocene." Peer-reviewed presentation at the SEAMO-SPAFA conference, Apr 2016, Bangkok, Thailand.

\ind Kretzler, I., J. Whittaker and B. Marwick 2015. ``Grand Challenges vs Actual Challenges: Text Mining Small and Big Data for Quantitative Insights".  Peer-reviewed presentation at the Society of American Archaeology conference, Apr 2015, San Francisco.

\ind Marwick, B. 2015 {\href{https://github.com/benmarwick/SAA2015-Open-Methods}{``Reproducible Research in Archaeology: Basic Principles and Common Tools"}}. Peer-reviewed presentation at the Society of American Archaeology conference, Apr 2015, San Francisco.

\ind De Boer, D., Zara Steinhart , Ben Marwick, David Bulbeck and Sue O'Connor. 2015 ``Stone Artefacts from Southeast Sulawesi: Technology Beyond the Toalean". Peer-reviewed presentation at the Society of American Archaeology conference, Apr 2015, San Francisco.

\ind Marwick, B. and Maloney, T. 2014 {\href{https://github.com/benmarwick/marwick-and-maloney-saa2014}{``Elliptical Fourier Analysis Unravels a Palimpsest of Point Technology  in the Kimberley, Western Australia"}}. Peer-reviewed presentation at the Society of American Archaeology conference, Apr 2014, Austin.

\ind Kretzler, I. and B. Marwick 2014 {\href{https://github.com/benmarwick/kretzler-and-marwick-saa2014}{``Understanding Archaeological History Through Textual Macroanalysis: The Role of Feminism in Gender Research"}}. Peer-reviewed presentation at the Society of American Archaeology conference, Apr 2014, Austin.

\ind Sonethongkham, S. and B. Marwick 2014 ``Variation in cores excavated from four rockshelter sites in Luang Prabang Province, Lao PDR". Peer-reviewed presentation at the Indo-Pacific Prehistory Association conference, Jan 2014, Siam Reap.

\ind Marwick, B.  and S. Sonethongkham 2014 ``Patterns in Holocene flaked artefact technology from excavations in Luang Prabang Province, Lao PDR" . Peer-reviewed presentation at the Indo-Pacific Prehistory Association conference, Jan 2014, Siam Reap.

\ind Marwick, B. C. Clarkson, S. O’Connor and S. Collins 2014 ``Pleistocene lithic technology from East Timor: remarkable long term stability in technological behaviours". Peer-reviewed presentation at the Indo-Pacific Prehistory Association conference, Jan 2014, Siam Reap.

\ind Hayes, E., R. Fullagar, C. Clarkson, M. Smith and B. Marwick 2014 ``Pleistocene evidence for seed grinding in Australia". Peer-reviewed presentation at the Indo-Pacific Prehistory Association conference, Jan 2014, Siam Reap.

\ind Steele, T, A. Mackay, K. Fitzsimmons, B. Marwick, J. Orton, S. Schwortz, M. Stahlschmidt 2014 ``Varsche Rivier 003: A Middle Stone Age site with Still Bay and Howiesons Poort assemblages in southern Namaqualand, South Africa." Peer-reviewed presentation at the European Society for the study of Human Evolution (ESHE). 18-20 September, 2014, Florence, Italy.

\ind Clarkson, C., M. Smith, B. Marwick, R. Fullagar, T. Manne, K. Lowe, X. Carah,  A. Florin, A.  Fairbairn, C. Pardoe and L. Wallis 2014 ``Excavations at Malakunanja II, northern Australia",  Peer-reviewed presentation at the Indo-Pacific Prehistory Association conference, Jan 2014, Siam Reap.

\ind Clarkson, C., M. Smith, R. Fullagar, B. Marwick, T. Manne, L. Wallis, Z. Jacobs, R. Roberts, K. Lowe, A. Florin, X. Carah, C. Pardoe and E. Hayes 2013 ``Report on new research at Madgedbebe (Malakunanja II)" . Peer-reviewed presentation at the Australian Archaeological Association Annual Conference, Dec 2013, Coff’s Harbour.

\ind Wallis, L., C. Pardoe, T. Manne, K. M. Lowe, J. Matthews, C.   Clarkson, B. Marwick, R. Fullagar and M. Smith 2013 ``Much more than just an old site: Human remains from the 2012 excavations at Madjedbebe, western Arnhem Land, Australia". Peer-reviewed presentation at the Australian Archaeological Association Annual Conference, Dec 2013, Coff’s Harbour.

\ind Lowe, K. L. A. Wallis, C. Pardoe, B. Marwick C. Clarkson, T. Manne, M. Smith and R. Fullagar. 2013 ``Ground-penetrating radar, GIS and burial practices in western Arnhem Land, Australia". Peer-reviewed presentation at the Australian Archaeological Association Annual Conference, Dec 2013, Coff’s Harbour.

\ind Hayes, E.  R. Fullagar, C. Clarkson, B. Marwick, M. Smith, L. Wallis and T. Manne, 2013 ``Pleistocene evidence for seed grinding in Australia". Peer-reviewed presentation at the Australian Archaeological Association Annual Conference, Dec 2013, Coff’s Harbour.

\ind Florin, A., C. Clarkson, A. Fairbairn, R. Fullagar, B. Marwick, L. Wallis, X. Carah, T. Manne and M. Smith. 2013 ``Archaeobotanical investigations into plant food use at Madjedbebe (Malakunanja II)". Peer-reviewed presentation at the Australian Archaeological Association Annual Conference, Dec 2013, Coff’s Harbour.

\ind Marwick, B. E. Hayes and C. Clarkson 2013 ``Movement of lithics by trampling: An experiment in the Malakunanja II sediments". Peer-reviewed poster at the Society of American Archaeology Annual Meeting, April 3-7, Honolulu, Hawaii. 2013

\ind Macy, K., B. Marwick, B. S. Hanyu, C. Conrad and A. Mackay 2013 ``Where did the dirt come from? Geochemical sediment tracing at Klipfonteinrand rockshelter, western South Africa". Peer-reviewed poster at the Society of American Archaeology Annual Meeting, April 3-7, Honolulu, Hawaii. 2013

\ind Bulbeck, D., B. Marwick, S. O'Connor, F. Aziz, A. Calo, J. Fenner, B. Hakim, A. Oktaviana and E. St Pierre 2013 ``Archaeology of Lake Towuti: Survey and Excavation in South Sulawesi". Peer-reviewed poster at the Society of American Archaeology Annual Meeting, April 3-7, Honolulu, Hawaii. 2013

\ind Marwick, B., P. Hiscock, P. Hughes and M. Sullivan. 2013 ``The use of mobile Geographic Information Systems for intensive archaeological survey in arid northeastern South Australia". Peer-reviewed presentation at the Computer Applications and Quantitative Methods in Archaeology Conference, University of Western Australia, Perth, Australia, March 18-21, 2013

\ind Marwick, B. ``How archaeologists explain (and how they ought to): Theory and practice of explanation in Australian archaeology". Peer-reviewed presentation at the Australian Archaeological Association, Wollongong, Australia, Dec 2012.

\ind Marwick, B, Anna Cohen, S. Kwak, K. Macy and A. Cowan 2011 ``Geoarchaeology of Iron Age ceramics at Tham Sua Cave, Northern Lao PDR". Peer-reviewed poster at the Society of American Archaeology Annual Meeting, Sacramento, CA.

\ind Marwick, B, T. Field, J. Martinez, P. Przystupa, K. Abbott, K. Macy, L. Minchk, P. Hughes and M. Sullivan 2010. ``Landscape archaeology in arid northeast South Australia: Preliminary investigations into relationships between site distributions, surface geology, water sources and wind patterns". Peer-reviewed poster at the Australian Association of Archaeology Annual Conference, Bateman’s Bay, New South Wales.

\ind Marwick, B, S. O’Connor and S. Collins 2010. ``Pleistocene-aged stone artefacts from Jerimalai, East Timor: Early modern human technology in island Southeast Asia". Peer-reviewed presentation at the 13th International Conference of the European Association of Southeast Asian Archaeologists (EurASEAA), Berlin, Germany.

\ind Marwick, B and Vanpheng Keopanna 2010. ``A pilot study of Geometric morphometric analysis of bronze Buddha craft traditions in the Lao PDR". Peer-reviewed presentation  at the 13th International Conference of the European Association of Southeast Asian Archaeologists (EurASEAA), Berlin, Germany.

\ind Marwick, B, 2010. ``Do Model-based explanations suit archaeology better than Inference to the Best Explanation?" Peer-reviewed presentation at the Society of American Archaeology Annual Meeting, St Louis, MO.

\ind Marwick, B, Ariel Auerbach and A. Cowan 2009. ``Geoarchaeology at Tham Sua Cave, Luang Prabang Province, Lao PDR". Peer-reviewed presentation at the Indo-Pacific Prehistory Association Congress, Hanoi, Vietnam.

\ind Brockwell, S., B. Marwick, P. Bourke, P. Faulkner, R. Willan 2009. ``Climate change records from North Australian cultural midden deposits: evidence from a pilot study of oxygen isotopes in mollusc shells". Peer-reviewed presentation  at the Australian Archaeological Association Annual Conference, Flinders University, Adelaide, South Australia.

% \ind Brockwell, S., P. Bourke, P. Faulkner, B. Marwick, B. Meehan. 2008. ``Climate Change and Behavioural Variability in Coastal Northern Australia". Peer-reviewed presentation at the World Archaeological Congress, Dublin,  Jul 2008.

% \ind Marwick, B. P. Hughes, P Hiscock, M. Sullivan, O. Macgregor 2008. ``Mobile Geographic Information Systems for Large-scale Intensive Archaeological Survey of Stone Artefact Scatters in Arid Australia". Peer-reviewed presentation at the Australian Archaeological Association Annual Conference, Noosa Dec 3-6 2008

% \ind Marwick, B. 2008. ``Measuring pre-processing in unretouched flaked stone artefact assemblages". Peer-reviewed presentation at the Australian Archaeological Association Annual Conference, Noosa Dec 3-6, Australia

% \ind Marwick, B. 2008. ``Hoabinhian flaked stone artefact palaeoeconomics and palaeoecology". Peer-reviewed presentation at the Society of American Archaeology, Vancouver, March 2008, Canada

% \ind Marwick, B. 2008 .``Ceramics of the three tributaries Luang Prabang, Lao PDR". Peer-reviewed presentation at the  Society of American Archaeology, Vancouver, March 2008, Canada

 \bigskip

 %% Talks at UW - scholarly

% \marginhead{\sffamily {\vskip 0.3em} invited  \newline scholarly \newline  talks \& \newline presentations \newline within UW}

% \noindent\emph{Invited scholarly talks \& presentations within UW \vspace{0.01in}}
%
% \medskip
%
% \ind Marwick, B. 2014. {\href{https://github.com/benmarwick/UW-eScience-reproducibility-social-sciences}{``Reproducible Research: A View from the Social Sciences".}}  UW eScience Institute, 9 Apr 2014. Invited presentation.
%
% \ind Marwick, B. 2014. {\href{https://github.com/benmarwick/CSSS-Primer-Reproducible-Research}{``Reproducible Research: A Primer for the Social Sciences".}}  UW Center for Statistics and the Social Sciences, 12 Mar 2014. Invited presentation.
%
% \ind Marwick, B. and I Kretzler 2014. {\href{https://github.com/benmarwick/Data-Science-at-UW-Poster}{``Text mining JSTOR: Quantitative approaches toward histories of science".} Poster presented to the UW eScience Institute Data Science Event, 7 Feb Oct 2014. Contributed presentation.
%
% \ind Marwick, B. 2014. ``Computational methods for the analysis of unstructured text". UW Department of Linguistics  Computational Linguistics Group, 4 Feb 2014. Invited presentation.
%
% \ind Marwick, B. ``Pleistocene language evolution and raw material transfers". UW Linguistics Department. 22 Nov 2013. Invited colloquium
%
% \ind Marwick, B. 2013. ``Mobile GIS for intensive archaeological survey of Holocene forager sites in arid South Australia". GIS Day Lightning Talk,  for the UW Geography Department 20 Nov 2013. Invited presentation.
%
% \ind Marwick, B. 2012 ``Cultural Phylogenetics of Religion using Thai Bronze Buddha Statues". UW Centre for Statistics and Social Sciences, 4 April 2012. Invited presentation.
%
%  \bigskip
%
%  %% Talks at UW
%
% % \marginhead{\sffamily {\vskip 0.3em} invited talks \newline on teaching \& learning \newline within UW}
%
% \noindent\emph{Invited talks on teaching and learning within UW \vspace{0.01in}}
%
% \medskip
%
%
% \ind Marwick, B. and I. Kretzler 2013. ``How to get students to read a lot. Distant reading in an archaeological theory seminar". Ignite presentation for the UW Center for Teaching and Learning eText workshop 24 Oct 2013 Invited presentation.
%
% \ind Marwick, B. 2013. ``Engaging large classes with technology, especially Canvas." Workshop presentation for the UW-IT Academic Services and the Center for Teaching and Learning, 7 Mar 2013.  Invited presentation.
%
% \ind Marwick, B. 2012. ``Engaging large classes with technology, especially Canvas." Presentation for the UW Center for Teaching and Learning's Large Class Collegium, 29 Aug 2012.  Invited presentation.

\medskip
