%%% A template to produce a nice-looking Curriculum Vitae.
%%% Originally from Kieran Healy <kjhealy@gmail.com>
%%% Kieran's source is at http://kjhealy.github.com/kjh-vita
%%%
%%% This source code has been adapted by
%%% Ben Marwick <benmarwick@gmail.com> and is largely
%%% determined by the instructions here:
%%% https://admin.artsci.washington.edu/promotion-and-tenure-documentation#curriculum
%%%

%%% ------------------------------------------------------------------------
%%% Requirements for this document that are included
%%%  in (or otherwise easily obtained) a modern tex distribution:
%%% ------------------------------------------------------------------------
%%% xelatex (I'm using MiKTeX & Texmaker)
%%% fontspec.sty
%%% hyperrref.sty
%%% xunicode.sty
%%% color.sty
%%% url.sty
%%% fancyhdr.sty
%%% memoir.cls
%%% fontawesome.sty
%%% gitinfo.sty
%%%
%%% ------------------------------------------------------------------------
%%% Requirements from https://github.com/kjhealy/latex-custom-kjh
%%% ------------------------------------------------------------------------
%%% org-preamble-xelatex.sty
%%% memoir-article-styles.sty
%%%
%%%
%%% ------------------------------------------------------------------------
%%% Note
%%%------------------------------------------------------------------------
%%% Because this is a hand-tweaked file, be on the look out for \medksip,
%%% \bigskip and \newpage commands here and there, which are used to balance
%%% the layout or avoid widows & orphans, etc. You should of course add or
%%% remove these as needed.
%%%------------------------------------------------------------------------

\documentclass[11pt,article,oneside]{memoir}
\usepackage{microtype}
\usepackage{org-preamble-xelatex}
\newfontfamily\fontawesome[Extension=.otf]{FontAwesome}
\usepackage{fontawesome5,url}
\usepackage{setspace}
\usepackage[footinfo]{gitinfo}
\input{../gitHeadInfo.gin}
\usepackage{xeCJK} %% for the Japanese characters
\setCJKmainfont[BoldFont=STSong,ItalicFont=STSong]{STSong}
\setCJKsansfont[BoldFont=STSong]{STSong}
\setCJKmonofont{STSong}

%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------

%% Change as needed.
\def\myauthor{Ben Marwick}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
%%%%%%%%  UW details
 \def\myaffiliation{University of Washington}
 \def\myaddress{Anthropology Department}
 \def\myemail{bmarwick@uw.edu}
 \def\myweb{http://faculty.washington.edu/bmarwick/ }
 \def\myphone{(206) 552-9450}
 \def\myfax{(206) 543-3285}
% \def\mytwitter{@benmarwick}
 \def\myversion{}
 \def\myrevision{}

%%%%%%%%  UOW details
% \def\myaffiliation{University of Wollongong}
% \def\myaddress{School of Earth and Environmental Sciences}
% \def\myemail{bmarwick@uow.edu.au}
% \def\myphone{(02) 4221 5455}
% \def\mytwitter{@benmarwick}


\def\myversion{}
\def\myrevision{}


%%%%%%%%  UW details
\def\myaffiliation{University of Washington}
%%%%%%%%  UOW details
% \def\myaffiliation{University of Wollongong}
\def\myauthor{Ben Marwick}
\date{} % not used (revision control instead)
\def\mykeywords{}




%%%------------------------------------------------------------------------
%%% Document
%%%------------------------------------------------------------------------
\begin{document}

%% Choose fonts for use with xelatex
%% Using free fonts with big glyph sets for maximum flexibility
%% http://www.linuxlibertine.org/index.php?id=2&L=1
%% http://font.ubuntu.com/

\setromanfont[Mapping={tex-text},
	Numbers={OldStyle},
	Ligatures={Common}]{Linux Libertine O}
\setsansfont[Mapping=tex-text,
	Ligatures={Common},
	Colour=AA0000]{Linux Biolinum O}
\setmonofont[Mapping=tex-text,Scale=0.72]{Ubuntu}

\newfontface\scheader[SmallCapsFont={Linux Libertine O},SmallCapsFeatures={Letters=SmallCaps}]{Linux Libertine O}

\newfontface\addressblock[Mapping={tex-text},
	Numbers={OldStyle},
	Ligatures={Common}]{Linux Libertine O}


%%%------------------------------------------------------------------------
%%% Local commands
%%%------------------------------------------------------------------------

%% Marginal header
%% Note: as the document goes on you may need to introduce a (gradually increasing)
%% \vspace element to keep the marginal header pleasingly aligned with the first
%% item in the body text. Like this: \marginhead{{\vskip 0.4em}Grants}, or
%% \marginhead{{\vskip 0.8em}Service}. Experiment as needed.
\newcommand{\marginhead}[1]{\marginpar{\textsf{{\footnotesize\vspace{-1em}\flushright #1}}}}


%% [optional] custom ampersand (font consistent with the one chosen above)
\newcommand{\amper}{{\fontspec[Scale=.95,Colour=AA0000]{Linux Libertine}\selectfont\&\,}}

%% No bullets on labels
\renewcommand{\labelitemi}{~}

%% Custom hanging indent for vita items
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
%\def\ind{\hangindent=18pt\hangafter=1 \noindent}
\def\labelitemi{~}
\renewcommand{\labelitemii}{~}

%%%------------------------------------------------------------------------
%%% Page layout
%%%------------------------------------------------------------------------

% These lines will insert git revision info in the footer, using the gitinfo
% package---see docs for gitinfo package for details. Comment out this line
% if you're not using git.
\pagestyle{kjh}
\thispagestyle{kjhgit}

%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------
\begin{minipage}[t]{2.95in}
 \flushright {\footnotesize
%%%%%%%%  UW details
 \href{http://depts.washington.edu/anthweb/}{Department of Anthropology} \\ Box 353100 \\ University of Washington  \\ \vspace{-0.05in} Seattle \textsc{wa} 98195-3100}

%%%%%%%%  UOW details
% \href{http://cas.uow.edu.au/}{Centre for Archaeological Science}\\ University of Wollongong  \\ \vspace{-0.05in} \textsc{NSW} 2500}

\end{minipage}
\hfill
%\begin{minipage}[t]{0.0in}
% dummy (needed here)
%\end{minipage}
\hfill
\begin{minipage}[t]{1.7in}
  \flushright \footnotesize  \addressblock \myphone \, {\fontawesome\char"F095} \\
%  {\scriptsize  \texttt{\href{http://twitter.com/benmarwick}{\mytwitter}} \, {\fontawesome\char"F099}  }\\
  {\scriptsize  \texttt{\href{mailto:\myemail}{\myemail}} \, {\fontawesome\char"F003}} \\
  %%{\scriptsize  \texttt{\href{\myweb}{\myweb}} \, {\fontawesome\char"F0AC}}
\end{minipage}

\medskip

%% Name
\noindent{\LARGE\scheader \textsc{bibliography}}
\reversemarginpar

\bigskip

% Bibliography: https://admin.artsci.washington.edu/promotion-and-tenure-documentation#curriculum

% The candidate's complete bibliography should be submitted, with entries listed in full bibliographic format, including range of page numbers or number of pages. In addition, the following items should be clearly indicated or distinguished:

% the type of each publication (article, book, review, monograph, technical report, etc.)
% the principal author(s) on multi-authored publications
% those publications which have had outside peer review before acceptance for publication
% a labeling of nonpublished material as "in press" or "accepted for publication," "submitted," or "work in progress" (note that "forthcoming" is ambiguous and should not be used)

\marginhead{\sffamily {{\vskip -0.35em} peer reviewed \newline journal articles}}

\ind \textbf{B. Marwick} (2025). \href{https://doi.org/10.1016/j.jas.2025.106281}{Is archaeology a science? Insights and imperatives from 10,000 articles and a year of reproducibility reviews.} \textit{Journal of Archaeological Science} 180, 106281. 

\ind Huan, F., Yang, S., \textbf{B. Marwick} et al. (2025). \href{http://doi.org/10.1007/s11442-025-2375-7}{Lithic miniaturization in South China since the terminal Pleistocene: A multivariate analysis of lithic reduction from Fodongdi, Fulin and Xiqiaoshan.} \textit{Journal of Geographic Science} 

\ind Ruan, Q., H. Li, P. Xiao, B. Li, H. Monod, A. Sumner, K. Zhao, J. Liu, Z. Jia, C. Wang, A. Fan, M. Moncel, \textbf{B. Marwick}, M. Peresani, Y. Wang, F. Chen, \& D. Delpiano (2025) \href{http://doi.org/10.1073/pnas.2418029122}{Quina lithic technology indicates diverse Late Pleistocene human dynamics in East Asia} \textit{Proceedings of the National Academy of Science} 122 (14) e2418029122 

\ind Hongliang Lu, Xinglong Zhang, Yaping Qin, Guobing Yang, Yun Chen, Pengchen Xu, Ming Huang, Ming Jiang, \textbf{B. Marwick} \& Yue Hu (2024). \href{http://doi.org/10.1080/01977261.2024.2435718}{New Evidence of Human Occupation in Southwest China Since 44,800 Years ago.} \textit{Lithic Technology} 

\ind Matzig D. N., \textbf{B. Marwick}, Riede F. and Warnock R. C. M. (2024). \href{http://doi.org/10.1098/rsos.240321}{A macroevolutionary analysis of European Late Upper Palaeolithic stone tool shape using a Bayesian phylodynamic framework.} \textit{Royal Society Open Science} 11240321 

\ind DiCiro, A., N. Mitchell, and \textbf{B. Marwick} (2024). \href{https://doi.org/10.5334/bha-697}{Everything is a Deposit: An interview with pioneering geoarchaeologist Julie K. Stein.} \textit{Bulletin of the History of Archaeology} 

\ind Hu, Y., \textbf{B. Marwick}, Lu, H. et al. (2024) \href{https://10.0.3.239/s12520-024-02022-4}{Lithic technologies at Guanyindong cave, Southwest China: diversity and innovation during the Chinese Middle Palaeolithic.} \textit{Archaeological and Anthropological Sciences} 16, 119 

\ind Stoudt S, Jernite Y, Marshall B, Marwick B, Sharan M, et al. (2024) \href{https://10.0.5.91/journal.pcbi.1012232}{Ten simple rules for building and maintaining a responsible data science workflow.} \textit{PLOS Computational Biology} 20(7): e1012232. 

\ind Park, G., Lombard, M., Chong, D., \textbf{B. Marwick} (2023). Variation in Use of East Asian Late Paleolithic Weapons: a Study of Tip Cross-sectional Area of Stemmed Points from Korea. \textit{Journal Paleolithic Archaeology} 6, 36 \href{https://doi.org/10.17605/osf.io/dqna8}{code \& data}

\ind Chen, Y. and \textbf{B. Marwick} (2023). Women in the Lab, Men in the Field? Correlations between Gender and Research Topics at Three Major Archaeology Conferences, \textit{Journal of Field Archaeology} \href{https://doi.org/10.17605/OSF.IO/ZFB36}{code \& data}

\ind Mackay, A., Saktura, R.B.K., O’Driscoll, C.A., Boyd, K., \textbf{B. Marwick} et al. (2023). The Middle Stone Age Sequence at Klipfonteinrand 1 (KFR1), Western Cape, South Africa. \textit{Journal of Paleolithic Archaeology} 6, 20 \href{http://doi.org/10.17605/OSF.IO/JBPFW}{code \& data}

\ind Shafizadeh, S. and \textbf{B. Marwick} (2023). Book review: The Upper Paleolithic of Zagros: by Sonia Shidrang, Tehran, Iran, Iranology Foundation, 2019, 5 chapters, 128 pp., many figures [Persian language]. \textit{Lithic Technology},

\ind  Yue, H. \textbf{B. Marwick}, Li Bo, et al. (2023). \href{https://doi.org/10.1016/j.jasrep.2022.103727}{Evidence of Levallois strategies on cores at Guanyindong cave, Southwest China during the Late Middle Pleistocene.} \textit{Journal of Archaeological Science: Reports} 

\ind Riede, F., A. Araujo, A, and \textbf{B. Marwick} (2022). \href{http://doi.org/10.1017/ehs.2022.18}{Robert C. Dunnell`s Systematics in Prehistory at 50.} \textit{Evolutionary Anthropology} \href{http://doi.org/10.17605/OSF.IO/JBPFW}{code \& data}

\ind Florin, A S., A. S. Fairbairn, M. Nango, D. Djandjomerr, Quan Hua, \textbf{B. Marwick}, D. C. Reutens, R. Fullagar, M. Smith, L. A. Wallis, C. Clarkson (2022). \href{https://doi.org/10.1016/j.quascirev.2022.107498}{65,000 years of changing plant food and landscape use at Madjedbebe, Mirarr country, northern Australia.} \textit{Quaternary Science Reviews} \href{http://doi.org/10.17605/OSF.IO/KPH5Z}{code \& data}

\ind Park, G., Wang, L., \& \textbf{B. Marwick} (2022). \href{https://doi.org/10.15184/aqy.2021.181}{How do archaeologists write about racism? Computational text analysis of 41 years of Society for American Archaeology annual meeting abstracts.} \textit{Antiquity}, 1-14. \href{http://doi.org/10.17605/OSF.IO/2N3RF}{code \& data}

\ind \textbf{B. Marwick}, Son, Pham Tanh, Brewer, Rachel, Wang, Li-Ying (2022) \href{https://osf.io/93fpa}{Tektite geoarchaeology in mainland Southeast Asia}. SocArXiv, 93fpa, ver. 6, peer-reviewed and recommended by \textit{PCI Archaeology}, https://osf.io/93fpa 

\ind Park, Gayoung \& \textbf{B. Marwick} (2022). \href{https://doi.org/10.1016/j.quascirev.2021.107312}{How did the introduction of stemmed points affect mobility and site occupation during the late Pleistocene in Korea?} \textit{Quaternary Science Reviews}, 277, 107312. \href{https://github.com/parkgayoung/koreapaleolithicmobilityoccupation}{code \& data}

\ind Dosseto, Anthony, and \textbf{B. Marwick} (2022). \href{https://doi.org/10.1016/j.quageo.2021.101235}{UThwigl — An R Package for Closed- and Open-System Uranium–Thorium Dating.} \textit{Quaternary Geochronology} 67: 101235. \href{https://github.com/tonydoss/UThwigl}{code \& data}

\ind Conrad, Cyler, Rasmi Shoocongdej, \textbf{B. Marwick}, et al. (2021). \href{https://doi.org/10.15184/aqy.2021.44}{Re-Evaluating Pleistocene–Holocene Occupation of Cave Sites in North-West Thailand: New Radiocarbon and Luminescence Dating.} \textit{Antiquity} \href{https://doi.org/10.17605/OSF.IO/J3Z6F}{code \& data}

\ind Wang, Li-Ying and \textbf{B. Marwick} (2021). \href{https://doi.org/10.1016/j.jas.2021.105471}{A Bayesian networks approach to infer social changes in burials in northeastern Taiwan during the European colonization period.} \textit{Journal of Archaeological Science} 134: 105471 \href{http://doi.org/10.17605/OSF.IO/XGA6N}{code \& data}

\ind \textbf{B. Marwick} and Prema Smith (2021). \href{http://dx.doi.org/10.1177/20539517211017304}{World Heritage sites on Wikipedia: Cultural heritage activism in a context of constrained agency.} \textit{Big Data \& Society} January–June: 1–19 \href{http://doi.org/10.17605/OSF.IO/AY27G}{code \& data}

\ind Florin, S.A., Roberts, P., \textbf{B. Marwick} et al. (2021) \href{https://doi.org/10.1038/s41559-020-01379-8}{Pandanus nutshell generates a palaeoprecipitation record for human occupation at Madjedbebe, northern Australia.} \textit{Nature Ecology and Evolution}. \href{http://doi.org/10.17605/OSF.IO/9TN4F}{code \& data}

\ind Hayes, E. H., Field, J. H., Coster, A. C. F., Fullagar, R., Matheson, C., Florin, S. A., Nango, M., Djandjomerr, D., \textbf{B. Marwick}, Wallis, L. A., Smith, M. A., \& Clarkson, C. (2021). \href{https://doi.org/10.1016/j.jasrep.2020.102754}{Holocene grinding stones at Madjedbebe reveal the processing of starchy plant taxa and animal tissue.} \textit{Journal of Archaeological Science: Reports}, 35, 102754.

\ind  \textbf{B. Marwick}, Pham Thanh Son, May Su Ko (2020). \href{https://doi.org/10.26721/spafajournal.v4i0.625}{Over research and ethics dumping in international archaeology.} \textit{SPAFA Journal} Vol 4 (2020)

\ind Nust D, Sochat V, \textbf{B. Marwick}, Eglen SJ, Head T, Hirst T, et al. (2020). \href{https://doi.org/10.1371/journal.pcbi.1008316}{Ten simple rules for writing Dockerfiles for reproducible data science.} \textit{PLoS Comput Biol} 16(11): e1008316.

\ind \textbf{B. Marwick} (2020). \href{https://doi.org/10.1016/j.ara.2020.100226}{Open access to publications to expand participation in archaeology}. \textit{Norwegian Archaeological Review} 

\ind Wang, L. and \textbf{B. Marwick} (2020). \href{https://doi.org/10.1016/j.ara.2020.100226}{Ornaments as indicators of social changes in northeastern Taiwan before and after European colonial period.} \textit{Archaeological Research in Asia} \href{http://doi.org/10.17605/OSF.IO/R8YGA}{code \& data}

\ind Wang, L. and \textbf{B. Marwick} (2020). \href{https://doi.org/10.1016/j.jasrep.2020.102554}{Investigating shape standardization using geometric morphometry of pottery from Iron Age northeastern Taiwan.} \textit{Journal of Archaeological Science: Reports} 33 \href{https://osf.io/abvgf/}{code \& data}

\ind Florin, S. Anna, Andrew S. Fairbairn, May Nango, Djaykuk Djandjomerr, \textbf{B. Marwick}, Richard Fullagar, Mike Smith, Lynley A. Wallis \& Chris Clarkson (2020). \href{https://doi.org/10.1038/s41467-020-14723-0}{The first Australian plant foods at Madjedbebe, 65,000–53,000 years ago}. \textit{Nature Communications} 11, 924. \href{https://doi.org/10.17605/OSF.IO/YDUZP}{code \& data}

\ind Schmidt, S.C. and \textbf{B. Marwick}, (2020). \href{http://doi.org/10.5334/jcaa.29}{Tool-Driven Revolutions in Archaeological Science}. \textit{Journal of Computer Applications in Archaeology}, 3(1), pp.18–32. \href{https://doi.org/10.17605/OSF.IO/RHVN5}{pre-print, code \& data}

\ind Yue Hu, Qijun Ruan, Jianhu Liu, \textbf{B. Marwick}, Bo Li (2019) \href{http://doi.org/10.1017/qua.2019.67}{Luminescence chronology and lithic technology of Tianhuadong Cave, an early Upper Pleistocene Paleolithic site in southwest China}. \textit{Quaternary Research} 94, 121-136.

\ind Yue Hu, \textbf{B. Marwick}, Jia-Fu Zhang, Xue Rui, Ya-Mei Hou, Wen-Rong Chen, Wei-Wen Huang, Bo Li (2019) \href{https://doi.org/10.1093/nsr/nwz192}{Robust technological readings identify integrated structures typical of the Levallois concept in Guanyindong Cave, South China} \textit{National Science Review} Volume 6, Issue 6, November 2019, Pages 1096–1099 

\ind \textbf{Marwick, B.}, Wang, L.-Y., Robinson, R., \& Loiselle, H. (2019). \href{https://doi.org/10.1017/aap.2019.38}{How to Use Replication Assignments for Teaching Integrity in Empirical Archaeology}. \textit{Advances in Archaeological Practice}, 8(1), 78-86. \href{https://osf.io/preprints/socarxiv/tsxbv/}{pre-print}, \href{https://doi.org/10.17605/OSF.IO/DBSW9}{code \& data}

\ind \textbf{Marwick, B.} (2019). \href{https://doi.org/10.15184/aqy.2019.131}{Galisonian logic devices and data availability: Revitalising Upper Palaeolithic cultural taxonomies.} \textit{Antiquity}, 93(371), 1365-1367. \href{https://osf.io/preprints/socarxiv/v8dej/}{pre-print}

\ind Stephens, L., Fuller, D., Boivin, N., Rick, T., Gauthier, N., Kay, A., \textbf{Marwick, B.}, ...  Ellis, E. (2019). \href{https://doi.org/10.1126/science.aax1192}{Archaeological assessment reveals Earth’s early transformation through land use.} \textit{Science}, 365(6456), 897–902. \href{https://dataverse.harvard.edu/dataverse/ArchaeoGLOBE}{pre-print, code \& data}

\ind Bulbeck, D., S., O’Connor, Fakhri, J. Fenner,  \textbf{B. Marwick}, Suryatman, F. Aziz, B. Hakim and U. Wibowo (2019) \href{https://doi.org/10.15184/aqy.2019.134}{Patterned and Plain Baked Clay in Pre-Pottery Contexts from Southeast Sulawesi, Indonesia.} \textit{Antiquity}, 93(371), 1284-1302 \href{https://osf.io/jn5tu/}{pre-print, code \& data}

\ind Hu, Y., \textbf{Marwick, B.}, Zhang, J.-F., Rui, X., Hou, Y.-M., Yue, J.-P., Li, B. (2018). \href{https://doi.org/10.1038/s41586-018-0710-1}{Late Middle Pleistocene Levallois stone-tool technology in southwest China.} \textit{Nature}  565, 82–85 \href{https://osf.io/erntj/}{code \& data}

\ind Clarkson, Chris, R. G. Roberts, Z. Jacobs, \textbf{B. Marwick}, R. Fullagar, L. J. Arnold \& Q. Hua 2018 \href{https://doi.org/10.1080/03122417.2018.1462884}{Reply to comments on Clarkson et al. (2017) Human occupation of northern Australia by 65,000 years ago} \textit{Australian Archaeology} Volume 84, Issue 1, pp. 84-89. \href{https://osf.io/qydc9/}{code \& data}

\ind Dominick, D., S. R. Wilson, C. Paton-Walsh, R. Humphries, E.-A. Guérette, M. Keywood, D. Kubistin, \textbf{B. Marwick} 2018 \href{http://doi.org/10.1016/j.atmosenv.2018.05.031}{Characteristics of airborne particle number size distributions in a coastal-urban environment}  \textit{Atmospheric Environment} Volume 186, August 2018, pp. 256-265.

\ind \textbf{Marwick, B.}, \& Birch, S. E. 2018 \href{https://doi.org/10.1017/aap.2018.3}{A Standard for the Scholarly Citation of Archaeological Data as an Incentive to Data Sharing}.  \textit{Advances in Archaeological Practice} Volume 6, Issue 2 May 2018, pp. 125-143. \href{https://doi.org/10.17605/OSF.IO/KSRUZ}{code \& data}

\ind Schaarschmidt, M., Fu, X., Li, B., \textbf{Marwick, B.}, Khaing, K., Douka, K., \& Roberts, R. G. 2018 \href{https://doi.org/10.1016/j.quageo.2018.01.001}{pIRIR and IR-RF dating of archaeological deposits at Badahlin and Gu Myaung Caves–First luminescence ages for Myanmar.} \textit{Quaternary Geochronology} DOI: https://doi.org/10.1016/j.quageo.2018.01.001

\ind \textbf{Marwick, B.}, Boettiger, C., \& Mullen, L. 2017 \href{https://doi.org/10.1080/00031305.2017.1375986}{Packaging data analytical work reproducibly using R (and friends).} \textit{The American Statistician} 72:1, 80-88 \href{https://doi.org/10.7287/peerj.preprints.3192v1}{preprint}

\ind  Clarkson, C., Jacobs, Z. \textbf{Marwick, B.}, and 19 others 2017 \href{http://dx.doi.org/10.1038/nature22968}{Human occupation of northern Australia by 65,000 years ago.} \textit{Nature} 547, pages 306–310 (20 July 2017) \href{https://doi.org/10.17605/OSF.IO/QWFCZ}{code \& data}

\ind  \textbf{Marwick, B.}, P. Hiscock, M. Sullivan, P. Hughes 2017 \href{http://doi.org/10.1016/j.jasrep.2017.07.004}{Landform boundary effects on Holocene forager landscape use in arid South Australia} \textit{Journal of Archaeological Science: Reports} 19, 864-874. \href{https://doi.org/10.17605/OSF.IO/V2MS9}{preprint}, \href{https://doi.org/10.17605/OSF.IO/EDZXS}{code \& data}

\ind  \textbf{Marwick, B.}, E. Hayes, C. Clarkson, R. Fullagar 2017 {\href{https://doi.org/10.1016/j.jas.2017.01.008}{Movement of lithics by trampling: An experiment in the Madjedbebe sediments, northern Australia} \textit{Journal of Archaeological Science}  79: 73–85 \href{https://doi.org/10.17605/OSF.IO/V2MS9}{preprint}, \href{https://doi.org/10.17605/OSF.IO/EDZXS}{code \& data}

\ind \textbf{Marwick, B.} 2017 {\href{http://dx.doi.org/10.1007/s10816-015-9272-9}{Computational Reproducibility in Archaeological Research: Basic Principles and a Case Study of Their Implementation}. \textit{Journal of Archaeological Method and Theory} 24: 424. DOI: 10.1007/s10816-015-9272-9. \href{https://doi.org/10.6084/m9.figshare.1563661}{code \& data}

\ind  Bulbeck, D., Aziz, F. A.,  O'Connor, S.,  Calo, A., Fenner, J. N., \textbf{Marwick, B.},  Feathers, J.,  Wood, R. \& Prastiningtyas, D. 2016. \href{http://dx.doi.org/10.1353/asi.2016.0017}{"Mortuary Caves and the Dammar Trade in the Towuti–Routa Region, Sulawesi, in an Island Southeast Asian Context."} \textit{Asian Perspectives} 55(2): 148-183.

\ind  \textbf{Marwick, B.}, Hannah Van Vlack; Cyler Conrad; Rasmi Shoocongdej; \newline Cholawit Thongcharoenchaikit; Seungki Kwak 2016 \href{http://dx.doi.org/10.1016/j.jas.2016.10.010}{Adaptations to sea level change and transitions to agriculture at Khao Toh Chong rockshelter, Peninsula Thailand} \textit{Journal of Archaeological Science} 77: 94–108 \href{https://osf.io/preprints/socarxiv/axxf8/}{preprint}, \href{https://dx.doi.org/10.6084/m9.figshare.2065602}{code \& data}

\ind  \textbf{Marwick, B.}, Chris Clarkson; Sue O'Connor; Sophie Collins 2016 {\href{http://dx.doi.org/10.1016/j.jhevol.2016.09.004}{Early Modern Human Lithic Technology from Jerimalai, East Timor.} \textit{Journal of Human Evolution} 101: 45–64 \href{http://dx.doi.org/10.6084/m9.figshare.985406}{code \& data}

\ind Steele, Teresa E., Alex Mackay, Kathryn E. Fitzsimmons,  \textbf{B. Marwick}, Jayson Orton, Steve Schwortz, Mareike C. Stahlschmidt 2016. Varsche Rivier 003:  {\href{http://www.paleoanthro.org/media/journal/content/PA20160100.pdf}{A Middle Stone Age site with Still Bay and Howiesons Poort assemblages in southern Namaqualand, South Africa} \textit{PaleoAnthropology} 2016: 100−163. \href{https://github.com/benmarwick/Steele_et_al_VR003_MSA_Pigments}{code \& data}

\ind Conrad, C., Higham, C., Eda, M. and \textbf{B. Marwick} 2016 \href{https://doi.org/10.1353/asi.2016.0013}{Paleoecology and Forager Subsistence Strategies During the Pleistocene-Holocene Transition: A Reinvestigation of the Zooarchaeological Assemblage from Spirit Cave, Mae Hong Son Province, Thailand}. \textit{Asian Perspectives} 55(1): 2-27. \href{http://hdl.handle.net/1928/26730}{code \& data}

\ind Tin Htut Aung, \textbf{B. Marwick}, C. Conrad 2015 \href{https://journals.lib.washington.edu/index.php/JIPA/article/view/14896}{Palaeolithic Zooarchaeology in Myanmar: A Review and Future Prospect} \textit{Journal of Indo-Pacific Archaeology} 39 DOI: 10.7152/jipa.v39i0.14896

\ind Kwak, S. and \textbf{B. Marwick} 2015 \href{http://journals.lib.washington.edu/index.php/JIPA/article/view/14708}{What did they cook? A preliminary investigation into culinary practices and pottery use in the central part of the Korean peninsula during the mid to late Holocene} \textit{Journal of Indo-Pacific Archaeology} 37  DOI: 10.7152/jipa.v37i0.14708

\ind Clarkson, C., Mike Smith, \textbf{B. Marwick}, Richard Fullagar, Lynley A. Wallis, Patrick Faulkner, Tiina Manne, Elspeth Hayes, Richard G. Roberts, Zenobia Jacobs, Xavier Carah, Kelsey M. Lowe, Jacqueline Matthews, S. Anna Florin 2015 \href{http://www.sciencedirect.com/science/article/pii/S0047248415000846}{The archaeology, chronology and stratigraphy of Madjedbebe (Malakunanja II): A site in northern Australia with early occupation} \textit{Journal of Human Evolution} 83: 46–64 DOI: 10.1016/j.jhevol.2015.03.014 \href{https://github.com/benmarwick/1989-excavation-report-Madjebebe}{code \& data}

\ind Lowe, K., Wallis, L., Pardoe, C., \textbf{Marwick, B}., Clarkson, C., Manne, T., Smith, M. and R. Fullagar 2014 \href{http://faculty.washington.edu/bmarwick/PDFs/Lowe_et_al_2014_MJB_GPR.pdf}{Ground-penetrating radar and burial practices in western Arnhem Land}, Australia. \textit{Archaeology in Oceania} 49:148-157.\newline  DOI: 10.1002/arco.5039 \href{https://github.com/benmarwick/Rocks-and-burials-at-Madjebebe}{code \& data}

\ind Mackay, A, T. Sumner, Z. Jacobs; \textbf{B. Marwick}, K. Bluff, M. Shaw. in press 2014.  \href{http://faculty.washington.edu/bmarwick/PDFs/Mackay_et_al_2014.pdf}{Putslaagte 1 (PL1), the Doring River, and the later Middle Stone Age in southern Africa's Winter Rainfall Zone}. \textit{Quaternary International} 350: 43-58 \href{https://github.com/benmarwick/Particle-size-analysis-Putslaagte-1}{code \& data}

\ind \textbf{Marwick, B.} 2013. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2013_JAA.pdf}{Multiple Optima in Hoabinhian flaked stone artefact palaeoeconomics and palaeoecology at two archaeological sites in Northwest Thailand} \textit{Journal of Anthropological Archaeology} 34(2): 553–564. \href{http://dx.doi.org/10.6084/m9.figshare.765252}{code \& data}

\ind Conrad, C., H. Van Vlack, \textbf{B. Marwick}, C. Thongcharoenchaikit, R. Shoocongdej, and B. Chaisuwan 2013 \href{http://faculty.washington.edu/bmarwick/PDFs/Conrad_et_al_2013_TNHMJ.pdf}{Summary of vertebrate and molluscan assemblages excavated from late-Pleistocene and Holocene deposits at Khao Toh Chong Rockshelter, Krabi, Thailand}. \textit{Thailand Natural History Museum Journal} 7(1): 11-22

\ind Brockwell, S., \textbf{B. Marwick}, P. Bourke, P. Faulkner and R. Willan. 2013. \href{http://faculty.washington.edu/bmarwick/PDFs/Brockwell_et_al_2013_AA.pdf}{Late Holocene Climate Change and Human Behavioural Variability in the Coastal Wet-Dry Tropics of Northern Australia: Evidence from a Pilot Study of Oxygen Isotopes in Molluscan Shells.} \textit{Australian Archaeology} 76: 21–33.

\ind Sullivan, M., T. Field, P. Hughes, \textbf{B. Marwick}, P. Przystupa, J. Feathers 2012. \href{http://faculty.washington.edu/bmarwick/PDFs/Sullivan_et_al_2012_OSL_dates_ODX.pdf}{OSL dates that inform late phases of dune formation and human occupation near Olympic Dam in northeastern South Australia.} \textit{Quaternary Australasia} 29(1): 4-11.

\ind Hughes, P., P. Hiscock, M. Sullivan and \textbf{B. Marwick}. 2011. \href{http://faculty.washington.edu/bmarwick/PDFs/Hughes_et_al_2011_JASSA.pdf}{An outline of archaeological investigations for the Olympic Dam Expansion in arid northeast South Australia}. \textit{Journal of the Anthropological Society of South Australia} 34:21-37

\ind \textbf{Marwick, B.} and M. Gagan 2011. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_and_Gagan_2011_QSR.pdf}{Late Pleistocene monsoon variability in northwest Thailand: an oxygen isotope sequence from the bivalve Margaritanopsis laosensis excavated in Mae Hong Son province.} \textit{Quaternary Science Reviews} 30(21-22): 3088-3098

\ind \textbf{Marwick, B.} 2010. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2010_WA_Wall-E.pdf}{Self-image, the long view and archaeological engagement with film: An animated case study.} \textit{World Archaeology} 42(3): 394–404

\ind \textbf{Marwick, B.} 2009a. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2009_AO_Pilbara.pdf}{Change or Decay? An interpretation of late Holocene archaeological evidence from the Hamersley Plateau, Western Australia.} \textit{Archaeology in Oceania} 44: 16-22

\ind \textbf{Marwick, B.}  2009b. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2009_QI.pdf}{Biogeography of Middle Pleistocene Hominins in Mainland Southeast Asia: A Review of Current Evidence.} \textit{Quaternary International} 202: 51–58

\ind \textbf{Marwick, B.} 2008a. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2008_Before_Farming.pdf}{Stone artefacts and recent research in the archaeology of mainland Southeast Asian hunter-gatherers.} \textit{Before Farming} 2008/4

\ind \textbf{Marwick, B.} 2008b. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2008_AA_3_Styles.pdf}{Three Styles of Darwinian Evolution in the Analysis of Stone Artefacts: Which one to use in Mainland Southeast Asia?} \textit{Australian Archaeology} 67: 79-86

\ind \textbf{Marwick, B.} 2008c. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2008_BIPPA.pdf}{Beyond typologies: The reduction thesis and its implications for lithic assemblages in Southeast Asia.} \textit{Bulletin of the Indo-Pacific Prehistory Association} 28: 108-116

\ind \textbf{Marwick, B.} 2008d. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2008_JAS.pdf}{Identifying variation in Hoabinhian lithic technology: An index of flake cortex distribution for the measurement of cobble reduction intensity.} \textit{ Journal of Archaeological Science} 35(5): 1189-1200.

\ind \textbf{Marwick, B.} 2007. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2007_SIJ.pdf}{Approaches to Stone Artefact Archaeology in Thailand: A Historical Review.} \textit{Silpakorn University International Journal} 7:49-88

\ind \textbf{Marwick, B.} 2005a. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2005_LHE.pdf}{The interpersonal origins of language: Social and linguistic implications of an archaeological approach to language evolution.} \textit{Linguistics and the Human Sciences} 1.2: 197-224.

\ind \textbf{Marwick, B.} 2005b. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2005_JAS.pdf}{Element Concentrations and Magnetic Susceptibility of Anthrosols: Indicators of Prehistoric Human Occupation in the inland Pilbara, Western Australia.} \textit{Journal of Archaeological Science} 32: 1357-1368.

\ind \textbf{Marwick, B.} 2003. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2003_CAJ.pdf}{Pleistocene exchange networks as evidence for the evolution of language.} \textit{Cambridge Archaeological Journa}l 17(1):67-81.

\ind \textbf{Marwick, B.} 2002a. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2002_Tempus.pdf}{Milly's Cave: Evidence for Human Occupation of the Inland Pilbara during the Last Glacial Maximum.} \textit{Tempus} 21-33.

\ind \textbf{Marwick, B.} 2002b. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2002_RWAM.pdf}{Evidence of Prehistoric Occupation of the Abrolhos Islands, Western Australia.} \textit{Records of the Western Australian Museum} 20(4):461-464.

\bigskip

\marginhead{\sffamily {{\vskip -0.35em} peer reviewed \newline book chapters}}

\ind \textbf{B. Marwick} and Li-Ying Wang (2022). \href{https://osf.io/preprints/socarxiv/s8z6u}{How to align disciplinary ideals with actual practices: Transparency and openness in archaeological science.} In: Ethan Watrall, Lynne Goldstein (eds) \textit{Digital Heritage and Archaeology in Practice}. University Press Florida.

\ind Bulbeck, D., and \textbf{B. Marwick} (2021). \href{https://doi.org/10.1093/oxfordhb/9780199355358.013.15}{Stone Industries of Mainland and Island Southeast Asia}. In Charles F. W. Higham and Nam C. Kim (eds) \textit{The Oxford Handbook of Early Southeast Asia}. Oxford University Press.

\ind Hayes, E., R. Fullagar, \textbf{B. Marwick} (2020) Australian Usewear/Residue Studies, Artefact Design and Multi-purpose Tools. In: Juan F. Gibaja, Joao Marreiros, Niccolò Mazzucco, Ignacio Clemente (eds) \textit{Hunter-Gatherers’ Tool-Kit: A Functional Perspective}. Cambridge Scholars Publishing. \href{https://doi.org/x10.17605/OSF.IO/MYBG2}{code \& data}

\ind Gray, C. T., \& \textbf{B. Marwick} (2019). \href{https://doi.org/10.1007/978-981-15-1960-4_8}{Truth, Proof, and Reproducibility: There’s No Counter-Attack for the Codeless}. In H. Nguyen (Ed.), \textit{Communications in Computer and Information Science 1150: Statistics and Data Science} (pp. 111–129). Springer.  \href{https://arxiv.org/abs/1907.05947}{pre-print}, \href{https://github.com/softloud/proof}{code \& data}

\ind \textbf{Marwick, B.} (2018) R Coding and Modelling. In Sandra L. López Varela (ed) \textit{Society of Archaeological Sciences Encyclopedia of Archaeological Science.}  John Wiley \& Sons, Inc. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick-2018-R-Coding-and-Modeling-The-Encyclopedia-of-Archaeological-Sciences.pdf}{PDF} \href{https://doi.org/10.1002/9781119188230.saseas0631}{DOI}

\ind Bulbeck, D. and \textbf{B. Marwick}. accepted, in press. Stone Industries of Mainland and Island Southeast Asia. In Nam Kim and Charles Higham (eds) \textit{Handbook of Southeast Asian Archaeology.} Oxford University Press.

\ind \textbf{Marwick, B.} 2018. \href{https://doi.org/10.1007/978-3-319-64407-3_4}{The Hoabinhian of Southeast Asia and its Relationship to Regional Pleistocene Lithic Technologies.} In Erick Robinson and Frédéric Sellet (eds) \textit{Lithic Technological Organization and Paleoenvironmental Change: Global and Diachronic Perspectives}. Springer. \href{https://doi.org/10.17605/OSF.IO/9PT8G}{preprint}

\ind \textbf{Marwick, B.} and B. Bouasisengpaseuth 2018. \href{https://doi.org/10.1007/978-1-4939-6521-2_8}{The history and practice of archaeology in Laos.} In Junko Habu, Peter Lape, John Olsen and Jing Zhichun (eds) \textit{ Handbook of East and Southeast Asian Archaeology.} Springer. \href{https://dx.doi.org/10.17605/OSF.IO/75ZHC}{preprint}

\ind Rokem, A. \textbf{B. Marwick}, and V. Staneva 2017 \href{https://www.practicereproducibleresearch.org/core-chapters/2-assessment.html}{Assessing Reproducibility.} In Justin Kitzes, Daniel Turek, Fatma Deniz (eds) \textit{The Practice of Reproducible Research: Case Studies and Lessons from the Data-Intensive Sciences.} University of California Press.

\ind Ram, K. and \textbf{B. Marwick} 2017 \href{https://www.practicereproducibleresearch.org/core-chapters/6-future.html}{Building Towards a Future Where Reproducible, Open Science is the Norm.} In Justin Kitzes, Daniel Turek, Fatma Deniz (eds) \textit{The Practice of Reproducible Research: Case Studies and Lessons from the Data-Intensive Sciences.} University of California Press.

\ind \textbf{Marwick, B.} 2017 \href{https://www.practicereproducibleresearch.org/case-studies/benmarwick.html}{Using R and Related Tools for Reproducible Research in Archaeology.} In Justin Kitzes, Daniel Turek, Fatma Deniz (eds) \textit{The Practice of Reproducible Research: Case Studies and Lessons from the Data-Intensive Sciences.} University of California Press. 

\ind Kretzler, I. and \textbf{B. Marwick} 2015 \href{http://faculty.washington.edu/bmarwick/PDFs/Kretzler_Marwick_2014_Chacmool.pdf}{Investigating Archaeologists' Engagement With Feminist Theory Using Textual Macroanalysis: 25 Years after Chacmool 1989}. \textit{Breaking barriers: Proceedings of the 47th Annual Chacmool Archaeological Conference November 7-9, 2014 Calgary, Alberta, Canada}. Robyn Crook, Kim Edwards and Colleen Hughes (eds). The University of Calgary, Chacmool Archaeological Association. pp. 158-168

\ind \textbf{Marwick, B.} 2013. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2013_DMAR.pdf}{Text mining and topic modeling for discovery of current issues in Anthropology using microblog content.} In  Yanchang Zhao and Yonghua Cen (eds) \textit{Data Mining Applications with R.} Elsevier. p. 63-93.

\ind \textbf{Marwick, B.}, R. Shoocongdej, C. Thongcharoenchaikit, B. Chaisuwan, C. Khowkhiew and S. Kwak.  2013. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_et_al_2013_community.pdf}{Hierarchies of engagement and understanding: Community engagement during archaeological excavations at Khao Toh Chong rockshelter, Krabi, Thailand.} In O’Connor, S (ed.) \textit{Transcending the Culture-Nature Divide in Cultural Heritage: Views from the Asia-Pacific Region}. Terra Australis, ANU E Press.

\ind \textbf{Marwick, B.} 2012. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2012_Buddha_cladistics.pdf}{Transmission of craft traditions in bronze Buddha manufacturing in ancient Thailand: A pilot study of the Griswold collection using cladistic techniques.} In Dominik Bonatz, Andreas Reinecke, Mai Lin Tjoa-Bonatz (eds.)\textit{ Connecting Empires and States: Selected Papers from the 13th Conference of the European Association of Southeast Asian Archaeologists.} National University of Singapore Press, Singapore. pp. 161-178.

\ind Mackay, A. and \textbf{B. Marwick} 2011. \href{http://faculty.washington.edu/bmarwick/PDFs/Mackay_and_Marwick_2011_timecost.pdf}{Costs and benefits in technological decision making under variable conditions: examples from the late Pleistocene in southern Africa.} In \textbf{B. Marwick} and A. Mackay (eds.) \textit{Keeping Your Edge: Recent Approaches to the Organisation of Stone Artefact Technology}. British Archaeological Reports.  pp. 119-134

\ind \textbf{Marwick, B.} 2008. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2008_EurASEAA.pdf}{Human Behavioural Ecology and Stone Artefacts in Northwest Thailand during the Terminal Pleistocene and Holocene.} Jean-Pierre Pautreau (ed) \textit{Southeast Asian Prehistory: The 11th EurASEAA}. Musée de Bougon: Paris. pp. 37-49.

\bigskip

\marginhead{\sffamily {{\vskip -0.35em} book reviews \newline (no outside \newline peer review)}}

\ind Shafizadeh, S and \textbf{Marwick, B.} 2023 Book review: Sonia Shidrang, 2019, The Upper Paleolithic of Zagros, Iranology Foundation, Tehran, Iran. 5 chapters. 128 pp,. Persian language \href{https://doi.org/10.1080/01977261.2023.2185741}{Lithic Technology}

\ind \textbf{Marwick, B.} 2018. \href{https://osf.io/preprints/socarxiv/v5du3/}{Book Review: "Uncertainty and sensitivity analysis in archaeological computational modeling" edited by Marieka Briuwer Burg, Hans Peeters, William A. Lovis} \textit{Journal of Anthropological Research}
} 

\ind \textbf{Marwick, B.} 2015a. \href{https://www.academia.edu/15214960/Review_of_Geoarchaeology_of_Aboriginal_Landscapes_in_Semi-Arid_Australia._Simon_J._Holdaway_and_Patricia_C._Fanning._2014._CSIRO_Collingwood._Geoarchaeology_Article_first_published_online_26_AUG_2015_DOI_10.1002_gea.21522}{Review of "Geoarchaeology of Aboriginal Landscapes in Semi-Arid Australia." Simon J. Holdaway and Patricia C. Fanning. 2014. CSIRO, Collingwood} \textit{Geoarchaeology}  DOI: 10.1002/gea.21522

\ind \textbf{Marwick, B.} 2015b. \href{http://intarch.ac.uk/journal/issue39/3/comms.cfm#tabs-3}{Films, digs and death: a review of the Project Eliseg video} \textit{Internet Archaeology} DOI: http://dx.doi.org/10.11141/ia.39.3.com3

\ind \textbf{Marwick, B.} 2009a. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2009_AA_Stark_Review.pdf}{Review of “Cultural Transmission and Material Culture: Breaking Down Boundaries.” Miriam Stark, Brenda Bowser and Lee Horne, eds. Tucson: University of Arizona Press, 2008.} \textit{American Anthropologist} 111(4): 540-541

\ind \textbf{Marwick, B.} 2009b. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2009_Shiner_review.pdf}{Review of "Place as Occupational Histories: An Investigation of the Deflated Surface Archaeological Record of Pine Point and Langwell Stations, Western New South Wales, Australia." by Justin Shiner. Archaeopress, Oxford, (2008).} \textit{Australian Archaeology} 69: 82

\ind \textbf{Marwick, B.} 2007. \href{http://faculty.washington.edu/bmarwick/PDFs/Evolution.pdf}{Review of “The origins and evolution of cultures”, by Peter Richerson and Robert Boyd. Oxford University Press, London, (2004).} \textit{The Australian Journal of Anthropology} 18(1): 97-98.

\ind \textbf{Marwick, B.} 2006. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2006_[B&R].pdf}{What can archaeology do with Boyd and Richerson’s Co-evolutionary program? Review of “Not By Genes Alone”, by Peter Richerson and Robert Boyd. Chicago University Press, Chicago, (2005)}. \textit{The Review of Archaeology} 26(2): 30-40.

\ind \textbf{Marwick, B.} 2005a. \href{http://faculty.washington.edu/bmarwick/PDFs/Uncovered.pdf}{Review of “Agency uncovered: Archaeological perspectives on social agency, power, and being human, edited by Andrew Gardner. UCL Press, London, (2004).} \textit{Anthropological Forum} 15(2): 203-204.

\ind \textbf{Marwick, B.} 2005b. \href{http://faculty.washington.edu/bmarwick/PDFs/Ghosts.pdf}{Review of “Marx’s ghost: Conversations with archaeologists”, by Thomas C. Patterson. Berg, Oxford. (2003)}. \textit{Anthropological Forum} 15(1): 92-94

\ind \textbf{Marwick, B.} 2003. \href{http://faculty.washington.edu/bmarwick/PDFs/Batavia.pdf}{Review of “Batavia’s graveyard. The true story of the mad heretic who lead history’s bloodiest mutiny”, by Mike Dash.} London: Weidenfeld and Nicolson. (2002). \textit{Limina} vol. 9: 236-240.

\ind \textbf{Marwick, B.} 2002. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2002_Dictionary.pdf}{Review of “A dictionary of archaeology”, edited by Ian Shaw and Robert Jameson. Oxford: Blackwell Publishers Ltd. (2002)} \textit{Australian Archaeology} 55: 50-51

\bigskip

\newpage

\marginhead{\sffamily {{\vskip -0.35em} editor-reviewed \newline publications \newline (no outside \newline peer review)}}

\ind \textbf{B. Marwick}, Li-Ying Wang, Kaylee Pruski, Eloise Potter,and Raelee Hampton (2021). \href{http://onlinedigeditions.com/publication/?m=16146&i=700116&p=46&ver=html5}{Views on the Future of Archaeological Ethics from the 2020 SAA Ethics Survey.} \textit{The SAA Archaeological Record} Volume 21, No. 2 March 2021, p. 45-54 

\ind Pruski, Kaylee, \textbf{B. Marwick}, Eloise Potter, Raelee Hampton, and Li-Ying Wang (2021). \href{http://onlinedigeditions.com/publication/?m=16146&i=700116&p=30&ver=html5}{Views on the Nine Principles of Archaeological Ethics from the 2020 SAA Ethics Survey.} \textit{The SAA Archaeological Record} Volume 21, No. 2 March 2021, p. 29-40 

\ind \textbf{Marwick, B.} 2020. \href{http://doi.org/10.24484/sitereports.69974}{考古学における研究成果公開の動向　－データ管理・方法の透明性・再現性} [Transparency, Reproducibility, Data Management and Methods for Archaeological Research Publications]. In 独立行政法人国立文化財機構奈良文化財研究所 2020 『デジタル技術による文化財情報の記録と利活用2』奈良文化財研究所研究報告24 [Nara Institute of Cultural Assets, National Institute of Cultural Assets, Independent Administrative Corporation 2020 “Recording and Utilization of Cultural Property Information via Digital Technologies Vol. 2 Open Science, Data Preservation, Intellectual Property, GIS” Nara Institute of Cultural Assets Research Report 24] [Japanese translation of an original English text]

\ind Riede, Felix, Astolfo G.M. Araujo Michael C. Barton Knut Andreas Bergsvik Huw S. Groucutt Shumon T. Hussain Javier Fernandez‐Lopez de Pablo Andreas Maier \textbf{Ben Marwick} Lydia Pyne Kathryn Ranhorn Natasha Reynolds Julien Riel‐Salvatore Florian Sauer Kamil Serwatka Annabell Zander (2020). \href{https://doi.org/10.1002/evan.21819}{Cultural taxonomies in the Paleolithic—Old questions, novel perspectives}. \textit{Evolutionary Anthropology} 29: 49– 52 

\ind \textbf{Marwick, B.}, Ellis, E., Stephens, L., N. Boivin (2019) \href{https://theconversation.com/surveying-archaeologists-across-the-globe-reveals-deeper-and-more-widespread-roots-of-the-human-age-the-anthropocene-122008}{Surveying archaeologists across the globe reveals deeper and more widespread roots of the human age, the Anthropocene} \textit{The Conversation} 29 Aug 2019.

\ind \textbf{Marwick, B.} (2019) \href{https://www.cambridge.org/core/blog/2019/08/19/how-to-make-the-data-and-code-for-your-manuscript-available-to-peer-reviewers-before-making-it-public/}{How to make the data and code for your manuscript available to peer reviewers before making it public.} Blog post for Cambridge University Press on the Cambridge Core Blog. 19 Aug 2019.

\ind \textbf{Marwick, B.} \& S. Pilaar Birch (2018) \href{https://www.cambridge.org/core/blog/2018/07/30/how-researchers-can-solve-the-bottle-opener-problem-with-compute-capsules/}{How researchers can solve the bottle-opener problem with compute capsules.} Blog post for Cambridge University Press on the Cambridge Core Blog. 30 Jul 2018. 

\ind \textbf{Marwick, B.}, L. Bo \& H. Yue (2018) \href{https://theconversation.com/new-dates-for-ancient-stone-tools-in-china-point-to-local-invention-of-complex-technology-106914}{New dates for ancient stone tools in China point to local invention of complex technology.} \textit{The Conversation} 19 Nov 2018 

\ind \textbf{Marwick, B.}, d`Alpoim Guedes, J., Barton, C. M., Bates, L. A., Baxter, M., Bevan, A., Bollwerk, E. A., Bocinsky, R. K., Brughmans, T., Carter, A. K., Conrad, C., Contreras, D. A., Costa, S., Crema, E. R., Daggett, A., Davies, B., Drake, B. L., Dye, T. S., France, P., Fullagar, R., Giusti, D., Graham, S., Harris, M. D., Hawks, J., Health, S., Huffer, D., Kansa, E. C., Kansa, S. W., Madsen, M. E., Melcher, J., Negre, J., Neiman, F. D., Opitz, R., Orton, D. C., Przstupa, P., Raviele, M., Riel-Savatore, J., Riris, P., Romanowska, I., Smith, J., Strupler, N., Ullah, I. I., Van Vlack, H. G., VanValkenburgh, N., Watrall, E. C., Webster, C., Wells, J., Winters, J., and Wren, C. D. (2017) \href{http://www.saa.org/Portals/0/SAA\_Record\_Sept\_2017\_Final\_LR.pdf\#page\=10}{Open science in archaeology}. \textit{SAA Archaeological Record}, 17(4), pp. 8-14. 

\ind \textbf{Marwick, B.} \& Z. Jacobs (2017) \href{https://theconversation.com/heres-the-three-pronged-approach-were-using-in-our-own-research-to-tackle-the-reproducibility-issue-80997}{Here’s the three-pronged approach we’re using in our own research to tackle the reproducibility issue.} \textit{The Conversation} 19 Jul 2017 

\ind \textbf{Marwick, B.}, Clarkson, C., Wallis, L. Fullagar, R., Z Jacobs (2017) \href{https://theconversation.com/buried-tools-and-pigments-tell-a-new-history-of-humans-in-australia-for-65-000-years-81021}{Buried tools and pigments tell a new history of humans in Australia for 65,000 years.} \textit{The Conversation} 19 Jul 2017 

\ind Eglen, S. J., \textbf{B. Marwick}, Y. O. Halchenko, M. Hanke, S. Sufi, P. Gleeson, R. A. Silver, A. P. Davison, L. Lanyon, M. Abrams, T. Wachtler, D. J. Willshaw, C. Pouzat and J.-B. Poline (2017). \href{http://www.nature.com/neuro/journal/v20/n6/full/nn.4550.html}{Toward standard practices for sharing computer code and programs in neuroscience.} \textit{Nature Neuroscience} 20(6): 770-773.

\ind \textbf{Marwick, B.} (2017). \href{https://blogs.uw.edu/openpub/2017/10/26/how-i-work-open-ben-marwick/}{How I work openly} \textit{Open @ UW Celebrating open scholarship at the University of Washington} blog post October 26, 2017 

\ind \textbf{Marwick, B.} (2017). \href{https://www.software.ac.uk/blog/2017-08-09-landscape-archaeology-and-reproducible-research-2017-berlin-summer-school}{Landscape archaeology and reproducible research at the 2017 Berlin Summer School} \textit{Software Sustainability Institute} blog post 9 August 2017 

\ind \textbf{Marwick, B.} (2017). \href{http://blog.revolutionanalytics.com/2017/04/r-is-for-archaeology.html}{R is for Archaeology: A report on the 2017 Society of American Archaeology meeting} \textit{Revolutions} blog post April 14, 2017 

\ind \textbf{Marwick, B.} 2016 \href{https://theconversation.com/how-computers-broke-science-and-what-we-can-do-to-fix-it-49938}{How computers broke science - and what we can do to fix it}. \textit{The Conversation} 15 Nov 2015.  Syndicated on \href{http://gizmodo.com/how-computers-broke-science-and-what-we-can-do-to-fix-i-1741649207}{Gizmodo}, \href{http://www.geekwire.com/2015/how-computers-broke-science-and-what-we-can-do-to-fix-it/}{Geekwire}, \href{http://qz.com/548730/computers-are-making-science-extremely-challenging-for-scientists/}{Quartz}, \href{http://www.netzpiloten.de/wissenschaft-computer-reproduzierbarkeit-probleme/}{Netzpiloten (in German)}, \href{http://filled-with-deities.hatenablog.jp/entry/2015/11/17/202013}{書は人間の夢を見るか (in Japanese)}, \href{https://theconversation.com/les-ordinateurs-nuisent-gravement-a-la-science-mais-il-est-possible-dy-remedier-1-52024}{The Conversation (in French)}, and \href{http://news.sciencenet.cn/htmlnews/2017/8/385497.shtm}{计算机对科学的挑战：我们该如何应对 ? ScienceNet.cn (in Chinese)}.

\ind \textbf{Marwick, B.} 2015. \href{https://www.software.ac.uk/blog/2016-09-26-archaeology-open-source-software-its-getting-easier}{Archaeology with open-source software. It's getting easier} \textit{Software Sustainability Institute} blog post 1 August 2015 

\ind \textbf{Marwick, B.} 2015. \href{https://software-carpentry.org/blog/2015/03/teaching-in-yangon.html}{Teaching in Yangon} \textit{Software Carpentry} blog post 25 March 2015 

\ind \textbf{Marwick, B.} and A. Mackay 2011. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_and_Mackay_2011_intro.pdf}{Keeping your edge: Recent approaches to the organisation of stone artefact technology.} In \textbf{B. Marwick} and A. Mackay (eds.) \textit{Keeping Your Edge: Recent Approaches to the Organisation of Stone Artefact Technology}. British Archaeological Reports.  pp. 1-4.

\ind White, J.C., Lewis, H., Bouasisengpaseuth, B., \textbf{Marwick, B.} and K. Arrell 2009. \href{http://faculty.washington.edu/bmarwick/PDFs/White_et_al_2009_Antiquity.pdf}{Archaeological investigations in northern Laos: New contributions to Southeast Asian prehistory.} \textit{Antiquity} 83(319) Project Gallery

\ind \textbf{Marwick, B.}, White, J.C., B. Bouasisengpaseuth 2009. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_et_al_2009_MMAP.pdf}{The Middle Mekong Archaeology Project and International Collaboration in Luang Prabang, Laos.} \textit{SAA Archaeological Record} 9 (3) 25-27

\ind \textbf{Marwick, B.} 2006. A Methodological Study of Technological Attributes in Hoabinhian Lithic Assemblages. In R. Shoocondej (ed.)  \textit{Social, Cultural and Environmental Dynamics in the Highlands of Pangmapha, Mae Hong Son Province: Integrated Archaeological Research into the Region}. Highland Archaeology Project in Pangmapha: Bangkok. pp. 231-244.

\ind \textbf{Marwick, B.} 2004. \href{http://faculty.washington.edu/bmarwick/PDFs/Marwick_2004_AACAI.pdf}{Future directions for research into open sites and rockshelters in the inland Pilbara.} \textit{Australian Association of Consulting Archaeologists Inc. Newsletter} 95:14-18.


\end{document}
